---
title: "BASL_v2_Ranalysis"
format: html
editor: visual
theme: superhero
page-layout: full
error: true
---

# SETUP

```{r}
# clear workspace
rm(list=ls());
ls();
```

```{r}
#| echo: true
#| output: false
# load required libraries
library(lme4);
library(Hmisc);
library(stats);
library(toolbox);
library(emmeans);
library(effects);
library(BayesRS);
library(extrafont);
library(showtext);
library(ggplot2);
library(viridis);
library(tidyverse);
library(DescTools);
library(paletteer);
library(BayesFactor);
library(RColorBrewer);
library(xtable);
library(corrplot);
library(psych);
library(sjPlot);
library(ggrepel);
library(png);
library(grid);
```

```{r}
# set global font
par(family="CMU Serif");
font_add("CMU Serif", "C:/Users/annal/Downloads/cmu/cmunrm.ttf");
showtext_auto();
```

```{r}
# set colour scheme
cols <- paletteer_d("MetBrewer::Degas");
cols2 <- paletteer_d("palettesForR::Named");
```

## Define Functions

### D Prime

```{r}
dPrime <- function(sbj, expectedResp, observedResp)
{
  sbjNumbers <- unique(sbj);
  dprimes <- vector(length=length(sbjNumbers), mode="numeric");
  log_beta <- vector(length=length(sbjNumbers), mode="numeric");
  c <- vector(length=length(sbjNumbers), mode="numeric");
  subjects <- vector(length=length(sbjNumbers), mode="integer");
  counter <- 1;
  for (s in sbjNumbers)
  {
    expectedRespCurrentSbj <- expectedResp[sbj==s];
    observedRespCurrentSbj <- observedResp[sbj==s];
    num_of_hits <- sum(observedRespCurrentSbj[expectedRespCurrentSbj==1])+.5;
    num_of_fa <- sum(observedRespCurrentSbj[expectedRespCurrentSbj==0])+.5;
    prop_of_hits <- num_of_hits/ (xtabs(~expectedRespCurrentSbj)[2]+1);
    prop_of_fa <- num_of_fa/ (xtabs(~expectedRespCurrentSbj)[1]+1);
    z_hits <- qnorm(prop_of_hits);
    z_fa <- qnorm(prop_of_fa); 
    dprimes[counter] <- round(z_hits - z_fa, digits = 3);
    log_beta[counter] <- round((z_fa^2 - z_hits^2)/2, digits = 3); #this is taken from Stanislaw and Todorov, PBR 1999. Log_beta=0 indicates no bias; negative values is bias for YES; positive values is bias for NO
    c[counter] <- round( -(z_hits + z_fa)/2, digits = 3); # this is taken again from Stanislaw and Todorov, PBR 1999, who note that c "...assumes that subjects respond yes when the decision variable exceeds the criterion and no otherwise; responses are based directly on the decision variable, which some researchers regard as more plausible than assuming that responses are based on a likelihood ratio [which the assumption behind beta] (Richardson, 1994). Another advantage of c is that it is unaffected by changes in d', whereas Beta is (Ingham, 1970; Macmil- lan, 1993; McNicol, 1972, pp. 63--64)". Similarly to log_beta, c=0 is no bias, negative c is bias for YES, negative c is bias for NO.
    subjects[counter] <- s;
    counter <- counter + 1;
  };
  data.frame(sbj=subjects, dprime=dprimes, log_beta=log_beta, c=c);
};
```

### Rounding

```{r}
round2 <- function(x, digits) {
  posneg = sign(x)
  z = abs(x)*10^digits
  z = z + 0.5 + sqrt(.Machine$double.eps)
  z = trunc(z)
  z = z/10^digits
  z*posneg
};
```

### LMER Export to LaTeX

```{r}
export_output <- function(model,name,pred_levels,
                         pred_type=c("categorical","continuous"),outcome_levels,
                         interaction=TRUE) {
  if (is.null(pred_type) || !length(pred_type) || !all(pred_type %in% c("categorical","continuous"))) {
    stop("'Predictor type' argument must be one of: 'categorical','continuous'")
  }
  
  # VARIABLES
  # trialn?
  vars <- all.vars(formula(model));
  if (vars[2] == "trialn") {
    trialn=TRUE;
  }  else {trialn=FALSE};
  
  # random effects?
  rand_vars <- toString(lme4::findbars(formula(model))[[1]])
  if (grepl("\\+",rand_vars)) {
    random_effects=TRUE
  } else {random_effects=FALSE};
  
  # interaction?
  formula_str <- toString(formula(model));
  if (grepl("\\*",formula_str)) {
    interaction=TRUE
  } else {interaction=FALSE};
  
  # FORMULA
  formula <- formula(summary(model));
  formula <- as.character(formula);
  formula <- paste(formula[2], formula[1], formula[3]);
  formula <- gsub("~", "$\\\\sim$", formula);
  formula <- gsub(" ","",formula);
  formula <- gsub("\\|", "\\\\textbar ", formula);
  formula <- gsub("expected", "string nature", formula);
  formula <- gsub("observed", "participant response", formula);
  name2 <- paste("\\multicolumn{5}{c}{\\textbf{",name,"}}",sep="");
  formula <- paste("\\multicolumn{5}{C{15cm}}{",formula,"}",sep="");
  formula <- data.frame(Groups=c(name2,formula),
                        Name=c("",""),
                        Variance=c("",""),
                        SD=c("",""),
                        Corr=c("",""));
  colnames(formula) <- c('\\textbf{Groups}','\\textbf{Name}',
                         '\\textbf{Variance}','\\textbf{SD}','\\textbf{Corr}');
  
  outcome_levels <- outcome_levels[-1];
  if (pred_type == "categorical") {
    pred_levels <- pred_levels[-1];
  }
  
  varcorr <- data.frame();
  if (random_effects) {
    # RANDOM EFFECTS
    varcorr <- data.frame(VarCorr(model));
    colnames(varcorr) <- c('Groups','Name','Var2','Variance','SD');
    if (length(outcome_levels) == 1) {
      varcorr$Corr <- c(0,varcorr$SD[nrow(varcorr)],0);
      colnames(varcorr) <- c('Groups','Name','Var2',
                             'Variance','SD','Corr');
      varcorr <- varcorr[-nrow(varcorr), ]
      varcorr <- varcorr[, -which(names(varcorr) == 'Var2')];
      varcorr[c('Variance','SD','Corr')] <- lapply(
        varcorr[c('Variance','SD','Corr')],
        function(x) round2(x,2));
      varcorr$Corr[varcorr$Corr == 0] <- "";
      varcorr$Groups[varcorr$Groups=='sbj_ID'] <- "";
      for (x in 1:length(outcome_levels)) {
        varcorr$Name[1+x] <- outcome_levels[x]
      };
      colnames(varcorr) <- c('\\textbf{Groups}','\\textbf{Name}',
                             '\\textbf{Variance}','\\textbf{SD}',
                             '\\textbf{Corr}');
      columns <- c('\\textbf{Random effects}','',
                   '\\textbf{Variance}','\\textbf{SD}','\\textbf{Corr}');
    }
    
    if (length(outcome_levels) == 2) {
      varcorr$Corr <- c(0,varcorr$SD[4],varcorr$SD[5]);
      varcorr$Corr2 <- c(0,0,varcorr$SD[6]);
      varcorr <- varcorr[-c((nrow(varcorr)-2):nrow(varcorr)), ]
      varcorr <- varcorr[, -which(names(varcorr) == 'Var2')];
      varcorr[c('Variance','SD','Corr','Corr2')] <- lapply(
        varcorr[c('Variance','SD','Corr','Corr2')],
        function(x) round2(x,2));
      varcorr$Corr[varcorr$Corr == 0] <- "";
      varcorr$Corr2[varcorr$Corr2 == 0] <- "";
      varcorr <- varcorr[, -which(names(varcorr) == 'Groups')];
      for (x in 1:length(outcome_levels)) {
        varcorr$Name[1+x] <- outcome_levels[x]
      };
      colnames(varcorr) <- c('\\textbf{Groups}','\\textbf{Name}',
                             '\\textbf{Variance}','\\textbf{SD}',
                             '\\textbf{Corr}');
      columns <- c('\\textbf{Random effects}','\\textbf{Variance}',
                   '\\textbf{SD}','\\textbf{Corr}','');
    };
    
    varcorr <- rbind(columns,varcorr)
    
    formula <- rbind(formula, varcorr);
  }
  
  # FIXED EFFECTS
  coefficients <- summary(model)$coefficients;
  coefs <- data.frame(coefficients);
  colnames(coefs) <- c('estimate','SE','z-value','p-value');
  
  coefs$sig <- "";
  coefs$sig[coefs$`p-value` < 0.1] <- " (.)";
  coefs$sig[coefs$`p-value` < 0.05] <- " (*)";
  coefs$sig[coefs$`p-value` < 0.01] <- " (**)";
  coefs$sig[coefs$`p-value` < 0.001] <- " (***)";
  
  coefs['p-value'] <- lapply(
    coefs['p-value'], 
    function(x) ifelse(
      abs(x)<=0.01,
      format(x,scientific=TRUE, digits=2),
      ifelse (x>0.04 & x<0.06, round2(x,3), round2(x,2))
    ));
  
  coefs[c('estimate','SE','z-value')] <- lapply(
    coefs[c('estimate','SE','z-value')], 
    function(x) ifelse(
      abs(x)<=0.01,
      format(x,scientific =TRUE, digits=2),
      round2(x,2)
    ));
  
  coefs$`p-value` <- paste(coefs$`p-value`,coefs$sig);
  coefs <- coefs[, -which(names(coefs) == 'sig')];
  
  columns <- c('\\textbf{Fixed effects}','$\\boldsymbol\\beta$','\\textbf{SE}',
               '\\textbf{z-value}','\\textbf{p-value}');
  rows <- c('(Intercept)');
  if (trialn) {
    rows <- c(rows,'scale(trialn)')
  };
  if (interaction == TRUE) {
    rows <- c(rows,outcome_levels);
  }
  for (level in pred_levels) {
    rows <- c(rows,level)
  }
  if (interaction == TRUE) {
    for (pred_level in pred_levels) {
      for (outcome_level in outcome_levels) {
        interaction <- paste(outcome_level,'*',pred_level,sep="")
        rows <- c(rows,interaction)
      }
    }
  }
  
  coefs <- cbind(rows,coefs);
  coefs <- rbind(columns,coefs);
  rownames(coefs) <- NULL;
  colnames(coefs) <- c('\\textbf{Groups}','\\textbf{Name}',
                       '\\textbf{Variance}','\\textbf{SD}','\\textbf{Corr}');
  
  global <- rbind(formula,coefs);
  
  filename <- paste('./analysis_tables/',name,".tex",sep="");
  
  if (random_effects) {
    hlines <- c(0,2,3,2+nrow(varcorr),3+nrow(varcorr),nrow(global));
  } else {
    hlines <- c(0,2,3,nrow(global));
  };
  
  print(xtable(global,auto=TRUE,booktabs=TRUE),
        file=filename,math.style.exponents=TRUE,latex.environments='center',
        include.rownames=FALSE,include.colnames=FALSE,
        tabular.environmen='tabularx',width="\\linewidth",
        hline.after=hlines,floating=FALSE,
        sanitize.text.function = function(x) {x});
  
  lines <- readLines(filename);
  lines <- gsub("\\\\begin\\{tabularx\\}\\{\\\\linewidth\\}\\{lllll\\}",
                "\\\\begin{tabularx}{\\\\linewidth}{{@{} >{\\\\RaggedRight}X*{5}{c}@{}}}",
                lines);
  lines <- gsub(" &  &  &  & ","",lines);
  lines <- gsub("\\\\hline","\\\\midrule",lines)
  writeLines(lines,filename);
};
```

## Set Directories

```{r}
# set working directory
setwd("C:/Users/annal/Documents/GitHub/affixproject");

# set analysis image output folder
output_folder <- "C:/Users/annal/Documents/Me/SISSA/BASL/BASL analysis/exp2";
```

## Input Participant IDs

```{r}
participants1 <- list('579e18fc4a84da00014c6f4f','5b6aa4aa0d748b0001fb5260','5c1a6bd8f9250d0001b7c589','5c437f6a4fe4f800016e3d52','5c840aedbad8fb000106cb44','5d696d1c55742f001af29220','5db16ce33990ed0014564873','5e248b6f0c0b31718a9d3f31','5e2b03f0005f2a02c5a64f7b','5e6449ae5932461d728d2152','5e8b85a61e16e9057a996e36','5e9dad3fd8d8010ac6a18620','5ebd8f8679146d0a116bc257','5ecba4b6ef75d53505406d57','5ed14691e983f5067842fd20','5eee55e93867d30a7771e616','5ef0b54037a90c618ad9e97f','5eff8b9ad19111064484eff7','5f1165307d03fb0009716b8e','5f21c29511084913913af654','5f316280965ec564c886f978','5f35782429beab53ef93cc2d','5f3d119b77d8ba0009a79558','5f5a5d4618746310515e2828','5f6f3d061214fe49ec2b9619','5f8af153e27f001bcc23ffc4','5f8b724dc36e8c2ac6d5fb6e','5f9c2359530d3e067a300bd6','5faacca24cd0384c1fa08be1','5fade36bdde8092117469a42','5fb2946df797088a8c405c2e','5ff3a2554cfb7d507511d89f','5ffab69a57132749844b8020','5ffd4230d96f6b2649d31f72','60204c263941fb63d9d794bc','602d2adcef81ce6b843da09b','60379326171365000ac6ae93','6046435099c3d00becdb2dfb','604d5e61486bd0622d2102c0','6057a8fe2d302939fc759940','60907b8091341e8724ba80ed','60a18093c5c040498d3addf8','60a8bd22d03adbe92cbb9a5e','60bf28df4926a8b6391df575','60c4a402716a8f9074fcd92e','60c715c89bb47f3847a690f0','60c873a65a9883b52f70db6c','60ca0b60979a23c83652c303','60cef349a1fff159b5d4853e','60d26e7cd9f0761e4d12b9f8','60d9dfd4dcc09cf57dc92cb1','60db9c9850c39eea109ef1d3','60e586145b73b702a608bace','60e5ac4f3d93f294f5fa543b','60f9739250a5c6f6e4726336','6102ee48644f517877d64d2b','6103cbc5310ffddfafa01661','6106ac34408681f3b0d07396','610d45e26c9b141264755d3c','61118c6d3c980e8b5b50e2fa','6117bb7900c0ba81f079a4ee','611d180283c1129def9284e6','611e00dc377e4fb7a27725e8','611e125063d1a52330225838','611fd297eb06449f7f0a06b9','61200d0d71bd5c0f9f9716b2','61242dd5be1a06b174975a1f','61248a51eefb6797024ecb85','612cc44439ccefbbd5d4b278','612cd9f34adcee82f65685a1','613054cf8dffc8bbb1fc9cc4','6134d182408816f4c1284496','6135f6887f5dd1472f7d3d6e','6136a1e1159dc808ad660d89','613758e7a80409ba7f5affb6','613ca0a2040055a4e87c5d71','6148b49d6ac652cefd310332','615c1372e7e639775817487e','6166ef334de9e433e83bfb79','616ad7ac6299f99ce33cdc78','616b567b3e605b7245a9aead','61717173748006894b2b54ff','6171946a19f6673fb215c0c7','6171f219ee27aa0e23d076aa','61758dd4ab7ec0d91a929f3d','628ed30ae7ff849e8bc91c86','631a1795de5efe7d3395caa3','63c5335da2b625ab1ade7e7c','6413799cf7721ee0ce637e09','646e0d2370c16a7561ae7dcb','6488afe97766c9083ffc3171','649264e0b601af80c5677791','6492c23a1a7735dfaab2b095','6495a5f76daf70e418baf5f7','6497e970e2621e753513a695','64e7533f36d388e8b31d3309','64e8bd55c9089d5bf26c90cd','64e8c14bbe184c20cb9d0583','64e9d6f596308448ac67bb95');
participants2 <- list('64f61553b5635b5e00595923','64f7a35c5f6503caaa59f79f','64fc701b223abd16ad5c940e','650330fa0cbc534b423f41e9','6505a9adbb769aeea736a2f5','650aed9eb9cc2c717ba70c30','6511e688100fd33b378fa688','651c59ec0cb6fef4208190f5','651eda4af4a809dbba0bb002','65352001dbe3e18eae5a8300','65361483b7f9881afa9b4cda','653d2df588326f6f627b8cb5','653fb764c9aed77c01457531','654632f222cb15acd453c0d3','65523123662559399b1aa48a','6557def45fc0ffbd46ad01de','655f5b404a09c686df3b0143','655f8b959477c803eb906622','65672c69a3737224f1d0bbfa','65774d879c53cc867fbe070c','657bfe6e245848c8fef0b389','6597e935328d41ae3aeef33b','6598994f0e7e5db183bfe3ee','659ada2d6df23a57d8e56752','65a97217d4fb858939a16b0f','65a97afe116a650acc588c5b','65abe33e1c79ea32da32ab0f','65ae78fc9cd81e8e26612cb2','65b901451577b2a0f18bc7ab','65b96f3bbecf5e7d0f5853cd','65c23d4dbad7238169292b54','65cba84263ac644fa79702ca','65cf6d92ac6f7932b1470fb4','65dce7715387badaf80e875d','65e7259b24116547c5512668','65f33b94cd6885d54029582d','65f7be6ac59662b24ac0f9b0','65fae6b84fa6b3101d2ca4b1','65fb18ef1c73590e7aaf1d48','65fc949678623ac83f926940','66031000461c44484ac359a8','660310c1b1a7ea09dee682e2','660678406bba1ade08345803','6606800e185d326591af6f7a','6606c9d692990fbf223f63bb','660c0d70a8f60acced0c8cc8','660c265dce47171c0dd7d359','66156fd87e14e8a60c007e17','66168e55cb60649609600268','6616a8636a12b432e8d914b5','6617af3304fe756a213cce24','661c24ab06db7f1ff0146700','661ff04db0e4a8222d5c4dd7','66271b4aaaf60fd058302f09','6634e4d4f1950b4dcd44d4d9','6634f754adfec54a4b1aaed4','66383ecf52e239b6f2ad54f4','663a5bb8f7f79c7e04abc9b3','663e08a82c273a8ea28be4e7','664b550820b57425a150d8e2','664b7cd6b5a772dd1eddca37','664f48afa42c9a4a7ed2bb88','664f70fcf77160132d600e2c','6658f0a58f1ee667f4264a93','6659ca4701d47b95a09ba736','6659ebda18cf5c43dbcc7354','665d94712b964d877bf9f132','665f79d15be62c63a74883d6','6661bf2ef4b2d0892ad7a007','6662d40766c8aa595834461d','666306b0bf2de127943c419f','6666a56ce75a18f29904e527','6666cf176a54945ba62e8ca9','6667488c5f46f3da0c085419','666f0fb7d9900bb03f5d99a1','666fd8b3dc9f2e1de77b5db4','6672ee650699d871b742ca6b','667437b20a6f1d1ebf68714b','667972671949d2e1c0c9ff54','667d631ef036f8ef4ff2f4f3','667dd7126e7a9073e0af73fd','6681625ff9dfa8a95bb0359d','6682b6d8a001b7f57c513ecc','66844cc1407c6afd0e100482','668553fe2efd22c91cf88fb9','6685e1541643171c04ec0e35','668992b2f868cb89829346c2','6692b87aad65e83d4230c307','6693f13e028361f102a9ed86','66951e094b5bd0caf94e844f','669cc52163cce3554e97d184','615c47639c04e360b0a76f58');
participants <- c(participants1,participants2);
```

# TESTING

```{r}
# importing testing data
data_all_testing <- read.csv("exp2_testing_preprocessed.csv",header=T,sep=",");
data_all_testing <- subset(data_all_testing, select = -c(X)) # remove redundant column added by Pavlovia
data_testing <- data_all_testing[data_all_testing$sbj_ID %in% participants,]; # n = 191 participants

# make some variables factors
data_testing$sbj_ID <- as.factor(data_testing$sbj_ID);
data_testing$task <- as.factor(data_testing$task);
data_testing$item <- as.factor(data_testing$item);
data_testing$testing_condition <- as.factor(data_testing$testing_condition);
data_testing$correct <- as.logical(data_testing$correct);

# change coding: 0 into 'within_lang' and 1 into 'between_lang'
data_expected <- replace(data_testing$expected, data_testing$expected == 0, 'within_lang');
data_expected <- replace(data_expected, data_expected == 1, 'between_lang');
data_testing$expected <- data_expected;
data_testing$expected <- as.factor(data_testing$expected);

data_observed <- replace(data_testing$observed, data_testing$observed == 0, 'within_lang');
data_observed <- replace(data_observed, data_observed == 1, 'between_lang');
data_testing$observed <- data_observed;
data_testing$observed <- as.factor(data_testing$observed);

# exclude 1 participant who filmed experiment
unique(data_testing$strategy[data_testing$sbj_ID=='666f0fb7d9900bb03f5d99a1']);
data_testing <- data_testing[!data_testing$sbj_ID %in% c('666f0fb7d9900bb03f5d99a1'),];
# now n=190
```

## Testing RTs

```{r}
IDs <- list(data_testing$sbj_ID);
IDs <- sapply(IDs, unique);
plot(density(data_testing$rt[data_testing$sbj_ID==IDs[1]],na.rm=TRUE),xlim=c(0,2200),ylim=c(0,0.01),xlab="RTs (ms)",main="",xaxt = "n",col=cols2[27],yaxs="i",lwd=1,cex.lab=1.5);
axis(1, at = c(0,200,400,600,800,1000,1200,1400,1600,1800,2000,2200));
for (x in 2:190) {
  lines(density(data_testing$rt[data_testing$sbj_ID==IDs[x]],na.rm=TRUE),col=cols2[x+26],lwd=1)
}; # good, centered around 800ms
data_testing_rt_means <- aggregate(data_testing$rt, list(data_testing$sbj_ID), FUN=mean, na.rm=TRUE);
summary(data_testing_rt_means$x); # good med & mean
plot(data_testing_rt_means$x, ylab="Mean participant RT (ms)",xlab="Participants",main="",xaxt = "n",pch=3,yaxs="i",ylim=c(0,2750))
# looks healthy overall

## problematic participant RTs ##
summary(data_testing$rt[data_testing$sbj_ID=="5e6449ae5932461d728d2152"]);
plot(data_testing$rt[data_testing$sbj_ID=="5e6449ae5932461d728d2152"],ylim=c(2000,22000));
plot(data_testing$rt[data_testing$sbj_ID=="5e6449ae5932461d728d2152"&data_testing$rt>2000]);
# include 5e6449ae5932461d728d2152: mean RT of 1502 slow, but only 10 trials too slow

summary(data_testing$rt[data_testing$sbj_ID=="667d631ef036f8ef4ff2f4f3"]);
plot(data_testing$rt[data_testing$sbj_ID=="667d631ef036f8ef4ff2f4f3"],ylim=c(2000,22000));
plot(data_testing$rt[data_testing$sbj_ID=="667d631ef036f8ef4ff2f4f3"&data_testing$rt>2000]);
# exclude 667d631ef036f8ef4ff2f4f3: mean RT of 1986 slow, and 35 trials too slow
data_testing <- data_testing[!data_testing$sbj_ID %in% c('667d631ef036f8ef4ff2f4f3'),];
data_testing_rt_means <- data_testing_rt_means[!data_testing_rt_means$Group.1 %in% c('667d631ef036f8ef4ff2f4f3'),]
# now n=189

summary(data_testing$rt[data_testing$sbj_ID=="6488afe97766c9083ffc3171"]);
# exclude 6488afe97766c9083ffc3171: mean RT of 175ms too fast
data_testing <- data_testing[!data_testing$sbj_ID %in% c('6488afe97766c9083ffc3171'),];
data_testing_rt_means <- data_testing_rt_means[!data_testing_rt_means$Group.1 %in% c('6488afe97766c9083ffc3171'),]
# now n=188

plot(data_testing$rt[data_testing$sbj_ID=="660c265dce47171c0dd7d359"]);
#fine to include: very long with the first item (50s!) but others all around 1s afterwards

summary(data_testing_rt_means$x);
```

## Testing Responses

```{r}
mean_yes <- aggregate(data_testing$observed,by=list(data_testing$sbj_ID), FUN=function(x) sum(x == 'within_lang'));
names(mean_yes) <- c("sbj_ID", "yes");
summary(mean_yes$yes);
#never said "yes": 660310c1b1a7ea09dee682e2
#always said "yes": 5faacca24cd0384c1fa08be1, 65f7be6ac59662b24ac0f9b0, 664b7cd6b5a772dd1eddca37
data_testing <- data_testing[!data_testing$sbj_ID %in% c('660310c1b1a7ea09dee682e2','5faacca24cd0384c1fa08be1','65f7be6ac59662b24ac0f9b0','664b7cd6b5a772dd1eddca37'),];
data_testing_rt_means <- data_testing_rt_means[!data_testing_rt_means$Group.1 %in% c('660310c1b1a7ea09dee682e2','5faacca24cd0384c1fa08be1','65f7be6ac59662b24ac0f9b0','664b7cd6b5a772dd1eddca37'),]
# now n=184
```

### 0M Responses

```{r}
data_testing_0M_yes <- aggregate(data_testing$observed[data_testing$testing_condition=='0M'], by=list(data_testing$sbj_ID[data_testing$testing_condition=='0M']), FUN = function(x) sum(x == 'within_lang'));
names(data_testing_0M_yes) <- c("sbj_ID","yes_0M");
data_testing_0M_yes$yes_0M <- data_testing_0M_yes$yes_0M/40*100; #transform into percent
summary(data_testing_0M_yes$yes_0M);
t.test(data_testing_0M_yes$yes_0M, mu=50);
# 0M "yes" not sig above chance
data_testing <- merge(data_testing,data_testing_0M_yes,by="sbj_ID");
```

### 1M Responses

```{r}
data_testing_1M_yes <- aggregate(data_testing$observed[data_testing$testing_condition=='1M'], by=list(data_testing$sbj_ID[data_testing$testing_condition=='1M']), FUN = function(x) sum(x == 'within_lang'));
names(data_testing_1M_yes) <- c("sbj_ID","yes_1M");
data_testing_1M_yes$yes_1M <- data_testing_1M_yes$yes_1M/40*100; #transform into percent
summary(data_testing_1M_yes$yes_1M);
t.test(data_testing_1M_yes$yes_1M, mu=50);
# sig above chance
data_testing <- merge(data_testing,data_testing_1M_yes,by="sbj_ID");
```

### 2M Responses

```{r}
data_testing_2M_yes <- aggregate(data_testing$observed[data_testing$testing_condition=='2M'], by=list(data_testing$sbj_ID[data_testing$testing_condition=='2M']), FUN = function(x) sum(x == 'within_lang'));
names(data_testing_2M_yes) <- c("sbj_ID","yes_2M");
data_testing_2M_yes$yes_2M <- data_testing_2M_yes$yes_2M/40*100; #transform into percent
summary(data_testing_2M_yes$yes_2M);
t.test(data_testing_2M_yes$yes_2M, mu=50);
# sig above chance
data_testing <- merge(data_testing,data_testing_2M_yes,by="sbj_ID");

data_testing_2M_aggr <- data_testing %>% 
  mutate(correct01 = case_when(correct == TRUE ~ 1,
                               correct == FALSE ~ 0),
         yesno01 = case_when(observed == 'between_lang' ~ 0,
                             observed == 'within_lang' ~ 1)) %>% 
  filter(testing_condition == '2M') %>% 
  group_by(expected, sbj_ID) %>% 
  dplyr::summarise(meanCorrect = mean(correct01), se = sd(correct01/sqrt(n())),
                   meanYes = mean(yesno01), se = sd(yesno01/sqrt(n()))) %>% 
  mutate(meanNo = 1 - meanYes);

data_testing_2M_aggr <- data_testing_2M_aggr %>%
  pivot_longer(
    cols = c(meanYes, meanNo),
    names_to = "response",
    values_to = "meanValue"
  );

data_testing_2M_aggr$response <- as.factor(data_testing_2M_aggr$response);

ggplot(data_testing_2M_aggr[ which(data_testing_2M_aggr$response=='meanYes'),], aes(x=expected, y=meanValue, fill=expected)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  geom_boxplot(width=0.1,position=position_dodge(width=1)) +
  scale_fill_manual(values=c(cols2[100],cols2[200]),
                    name="Participant response",labels=c("Between-language","Within-language")) +
  scale_x_discrete(labels=c('Between-language', 'Within-language')) +
  labs(x = "String nature", y = 'Proportion of "within-language" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="none",
        legend.background=element_rect(fill=NA));
```

### 2M Scores

```{r}
data_testing_2M_means <- aggregate(data_testing$correct[data_testing$testing_condition=='2M'], list(data_testing$sbj_ID[data_testing$testing_condition=='2M']), FUN=mean, na.rm=TRUE);
names(data_testing_2M_means) <- c("sbj_ID","score_2M");

ggplot(data_testing_2M_means, aes(x="", y=score_2M)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_boxplot(fill="grey") +
  ylim(0,1) +
  labs(y='Participant 2M scores') +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));

summary(data_testing_2M_means$score_2M);
var(data_testing_2M_means$score_2M); #var=0.006
plot(data_testing_2M_means$score_2M,pch=3,ylim=c(0,1));
abline(h=0.5, lty=5); # clustered around chance
hist(data_testing_2M_means$score_2M); # normally distributed
t.test(data_testing_2M_means$score_2M, mu=0.50);
# not sig different from chance
data_testing <- merge(data_testing,data_testing_2M_means,by="sbj_ID");
```

### d' Computations

```{r}
data_testing_2M <- data_testing[data_testing$testing_condition == '2M',];

data_testing_2M$expected_bi[data_testing_2M$expected == "between_lang"] <- 0;
data_testing_2M$expected_bi[data_testing_2M$expected == "within_lang"] <- 1;
data_testing_2M$observed_bi[data_testing_2M$observed == "between_lang"] <- 0;
data_testing_2M$observed_bi[data_testing_2M$observed == "within_lang"] <- 1;

dprimes2M <- dPrime(data_testing_2M$sbj_ID, data_testing_2M$expected_bi, data_testing_2M$observed_bi);
names(dprimes2M) <- c("sbj_ID","dprime","log_beta","c");
summary(dprimes2M);
# mean(d') = -0.03, mean(c) = -0.35
data_testing <- merge(data_testing,dprimes2M,by="sbj_ID");
cor.test(data_testing$dprime,data_testing$c, method="pearson"); 
# significant but tiny positive correlation
# more "YES" responses doesn't help you respond accurately

testing_short <- data_testing[!duplicated(data_testing$sbj_ID), ];
t.test(testing_short$dprime, mu=0);
# not sig different from chance
t.test(testing_short$c, mu=0);
# sig above chance
```

### "Yes" Responses across Conditions

```{r}
# evaluating the differences between conditions
data_testing_conditions <- merge(data_testing_0M_yes,data_testing_1M_yes, by='sbj_ID');
data_testing_conditions <- merge(data_testing_conditions,data_testing_2M_yes, by='sbj_ID');
conditions_table <- table(data_testing$testing_condition, data_testing$observed);
chisq.test(conditions_table);
data_testing_conditions <- data_testing_conditions %>%
  gather(condition, score, -sbj_ID);
data_testing_conditions$score <- data_testing_conditions$score/100;

# plotting all "yes" responses across conditions
ggplot(data_testing_conditions, aes(x = condition, y = score, color = condition)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_jitter(width = 0.1, height = 0, alpha = 0.3,color= "black",size=2) +
  labs(x = "Condition", y = 'Proportion of "yes" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20)) +
  ylim(0,1.01) +
  stat_summary(geom = "point",fun = "mean",col = "red",size = 4,shape = 19) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.1,col="red",position = position_dodge(width = 0.5)) +
  scale_x_discrete(labels=c("0M", "1M", "2M"));

# 2M accuracy*RTs
cor.test(data_testing_2M_means$score_2M, data_testing_rt_means$x, method="pearson");
# non-significant correlation
```

## Strategies

```{r}
strats <- subset(data_testing, select = c(sbj_ID, strategy));
strats <- strats[!duplicated(strats),];
write.csv(strats,"BASL_exp2_strats.csv", row.names = FALSE);
```

### Chunks

```{r}
chunkID_strategists <- list('5ed14691e983f5067842fd20','5ef0b54037a90c618ad9e97f','602d2adcef81ce6b843da09b','6046435099c3d00becdb2dfb','6057a8fe2d302939fc759940','60bf28df4926a8b6391df575','60d26e7cd9f0761e4d12b9f8','60db9c9850c39eea109ef1d3','611d180283c1129def9284e6','6134d182408816f4c1284496','6136a1e1159dc808ad660d89','6148b49d6ac652cefd310332','6171946a19f6673fb215c0c7','628ed30ae7ff849e8bc91c86','631a1795de5efe7d3395caa3','63c5335da2b625ab1ade7e7c','6495a5f76daf70e418baf5f7','64e9d6f596308448ac67bb95','65361483b7f9881afa9b4cda','65672c69a3737224f1d0bbfa','65a97217d4fb858939a16b0f','65c23d4dbad7238169292b54','65dce7715387badaf80e875d','65e7259b24116547c5512668','660c265dce47171c0dd7d359','661c24ab06db7f1ff0146700','6634f754adfec54a4b1aaed4','664f70fcf77160132d600e2c','6661bf2ef4b2d0892ad7a007','666306b0bf2de127943c419f','668992b2f868cb89829346c2','6692b87aad65e83d4230c307');
data_chunkIDstrategists <- data_testing[data_testing$sbj_ID %in% chunkID_strategists,];
data_chunkIDstrategists <- data_chunkIDstrategists[data_chunkIDstrategists$testing_condition=='2M',];
data_chunkIDstrategists <- data_chunkIDstrategists[!duplicated(data_chunkIDstrategists$sbj_ID), ];
data_chunkIDstrategists$strat <- "chunkID";
summary(data_chunkIDstrategists$score_2M);
t.test(data_chunkIDstrategists$score_2M, mu=0.50);
# not sig different from chance
summary(data_chunkIDstrategists$dprime);
summary(data_chunkIDstrategists$c);
# dprime:0.01 c:-0.48

ggplot(data_chunkIDstrategists, aes(x="", y=score_2M)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,fill="gold1") +
  geom_boxplot(width=0.1,fill="gold1") +
  ylim(0,1) +
  labs(y='Participant 2M scores') +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### Intuition

```{r}
intuition_strategists <- list('579e18fc4a84da00014c6f4f','5c840aedbad8fb000106cb44','5d696d1c55742f001af29220','5e248b6f0c0b31718a9d3f31','5e2b03f0005f2a02c5a64f7b','5ebd8f8679146d0a116bc257','5eee55e93867d30a7771e616','5f1165307d03fb0009716b8e','5f21c29511084913913af654','5f35782429beab53ef93cc2d','5f6f3d061214fe49ec2b9619','5f8af153e27f001bcc23ffc4','5f8b724dc36e8c2ac6d5fb6e','5fade36bdde8092117469a42','5ffd4230d96f6b2649d31f72','60379326171365000ac6ae93','604d5e61486bd0622d2102c0','60907b8091341e8724ba80ed','60c873a65a9883b52f70db6c','60ca0b60979a23c83652c303','60d9dfd4dcc09cf57dc92cb1','60e586145b73b702a608bace','60e5ac4f3d93f294f5fa543b','60f9739250a5c6f6e4726336','6102ee48644f517877d64d2b','6106ac34408681f3b0d07396','610d45e26c9b141264755d3c','611e00dc377e4fb7a27725e8','61242dd5be1a06b174975a1f','61248a51eefb6797024ecb85','612cc44439ccefbbd5d4b278','613054cf8dffc8bbb1fc9cc4','613758e7a80409ba7f5affb6','613ca0a2040055a4e87c5d71','6166ef334de9e433e83bfb79','616ad7ac6299f99ce33cdc78','61717173748006894b2b54ff','6413799cf7721ee0ce637e09','646e0d2370c16a7561ae7dcb','649264e0b601af80c5677791','6492c23a1a7735dfaab2b095','6497e970e2621e753513a695','64e8bd55c9089d5bf26c90cd','64e8c14bbe184c20cb9d0583','64f7a35c5f6503caaa59f79f','6505a9adbb769aeea736a2f5','650aed9eb9cc2c717ba70c30','65352001dbe3e18eae5a8300','653fb764c9aed77c01457531','654632f222cb15acd453c0d3','65523123662559399b1aa48a','6557def45fc0ffbd46ad01de','655f5b404a09c686df3b0143','655f8b959477c803eb906622','657bfe6e245848c8fef0b389','6597e935328d41ae3aeef33b','6598994f0e7e5db183bfe3ee','659ada2d6df23a57d8e56752','65a97afe116a650acc588c5b','65b96f3bbecf5e7d0f5853cd','65cf6d92ac6f7932b1470fb4','65f33b94cd6885d54029582d','66031000461c44484ac359a8','6606c9d692990fbf223f63bb','66168e55cb60649609600268','661ff04db0e4a8222d5c4dd7','663e08a82c273a8ea28be4e7','664f48afa42c9a4a7ed2bb88','6659ca4701d47b95a09ba736','665f79d15be62c63a74883d6','6662d40766c8aa595834461d','6666cf176a54945ba62e8ca9','6667488c5f46f3da0c085419','6672ee650699d871b742ca6b','667dd7126e7a9073e0af73fd','6681625ff9dfa8a95bb0359d','66844cc1407c6afd0e100482','6693f13e028361f102a9ed86','66951e094b5bd0caf94e844f');
data_intuitionstrategists <- data_testing[data_testing$sbj_ID %in% intuition_strategists,];
data_intuitionstrategists <- data_intuitionstrategists[data_intuitionstrategists$testing_condition=='2M',];
data_intuitionstrategists <- data_intuitionstrategists[!duplicated(data_intuitionstrategists$sbj_ID), ];
data_intuitionstrategists$strat <- "intuition";
summary(data_intuitionstrategists$score_2M);
t.test(data_intuitionstrategists$score_2M, mu=0.50);
# not sig different from chance
summary(data_intuitionstrategists$dprime);
summary(data_intuitionstrategists$c);
# dprime:-0.07 c:-0.29

ggplot(data_intuitionstrategists, aes(x="", y=score_2M)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,fill="palevioletred") +
  geom_boxplot(width=0.1,fill="palevioletred") +
  ylim(0,1) +
  labs(y='Participant 2M scores') +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### Comparison

```{r}
scores_strategies <- rbind(data_chunkIDstrategists,data_intuitionstrategists);
ggplot(scores_strategies, aes(x=strat, y=score_2M, fill=strat)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  geom_boxplot(width=0.1,position=position_dodge(width=1)) +
  ylim(0,1) +
  scale_fill_manual(values=c("gold1","palevioletred")) +
  scale_x_discrete(labels=c('Chunk ID', 'Intuition')) +
  labs(x="Strategy used",y="Participant 2M scores") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="none",legend.background=element_rect(fill=NA));
```

# FAMILIARITY

```{r}
data_all_familiarity <- read.csv("exp2_familiarity_preprocessed.csv",header=T,sep=",");
data_all_familiarity <- subset(data_all_familiarity, select = -c(X)) # remove redundant column added by Pavlovia
data_familiarity <- data_all_familiarity[data_all_familiarity$sbj_ID %in% participants,]; # n = 187 participants
data_familiarity <- data_familiarity[!data_familiarity$sbj_ID %in% c('667d631ef036f8ef4ff2f4f3','6488afe97766c9083ffc3171','666f0fb7d9900bb03f5d99a1','660310c1b1a7ea09dee682e2','5faacca24cd0384c1fa08be1', '65f7be6ac59662b24ac0f9b0', '664b7cd6b5a772dd1eddca37'),];

# make some variables factors
data_familiarity$sbj_ID <- as.factor(data_familiarity$sbj_ID);
data_familiarity$task <- as.factor(data_familiarity$task);
data_familiarity$correct <- as.logical(data_familiarity$correct);
data_familiarity$target <- as.factor(data_familiarity$target);
data_familiarity$confound <- as.factor(data_familiarity$confound);
```

## Familiarity Accuracy

```{r}
data_familiarity_means <- aggregate(data_familiarity$correct, list(data_familiarity$sbj_ID), FUN=mean);
colnames(data_familiarity_means)[colnames(data_familiarity_means)=="Group.1"]="sbj_ID";
colnames(data_familiarity_means)[colnames(data_familiarity_means)=="x"]="fam_mean";
summary(data_familiarity_means$fam_mean);
hist(data_familiarity_means$fam_mean); # mostly normally distributed
t.test(data_familiarity_means$fam_mean, mu=0.50);
# sig above chance
var(data_familiarity_means$fam_mean);
data_familiarity <- merge(data_familiarity,data_familiarity_means,by="sbj_ID");

# familiarity accuracy violin plot
ggplot(data_familiarity_means, aes(y=fam_mean, x=x)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_violin(alpha=0.75,fill="orchid4") +
  geom_boxplot(width=0.1,fill="orchid4") +
  ylim(0,1) +
  scale_fill_manual(values=cols2[350]) +
  labs(y = 'Proportion of correct familiarity responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),legend.position = "none",
        axis.title.x=element_blank(),axis.text.x=element_blank(),
        axis.ticks.x=element_blank());
```

## Familiarity RTs

```{r}
IDs <- list(data_familiarity$sbj_ID);
IDs <- sapply(IDs, unique);
plot(density(data_familiarity$rt[data_familiarity$sbj_ID==IDs[1]]),xlim=c(0,4000),ylim=c(0,0.01),xlab="Familiarity RTs (ms)",main="",xaxt = "n",col=cols2[1],lwd=2,yaxs="i");
axis(1, at = c(0,500,1000,1500,2000,2500,3000,3500,4000));
for (x in 2:184) {
  lines(density(data_familiarity$rt[data_familiarity$sbj_ID==IDs[x]]),col=cols2[x],lwd=2)
};
data_familiarity_rt_means <- aggregate(data_familiarity$rt, list(data_familiarity$sbj_ID), FUN=mean, na.rm=TRUE);
summary(data_familiarity_rt_means$x);

# familiarity accuracy*RTs
cor.test(data_familiarity_means$fam_mean, data_familiarity_rt_means$x, method="pearson")
# slower at responding = better accuracy
```

## Comparisons with Testing

```{r}
# familiarity accuracy*testing accuracy
cor.test(data_familiarity_means$fam_mean, data_testing_2M_means$score_2M, method="pearson");
# no correlation

# familiarity accuracy by testing strategy
data_strategistsfam <- data_familiarity_means;
data_strategistsfam$strat[data_strategistsfam$sbj_ID %in% intuition_strategists] <- 'intuition';
data_strategistsfam$strat[data_strategistsfam$sbj_ID %in% chunkID_strategists] <- 'chunks';
data_strategistsfam$strat[data_strategistsfam$sbj_ID %in% chunkID_strategists] <- 'chunks';
data_strategistsfam$strat <- data_strategistsfam$strat %>% replace_na('other');

summary(data_strategistsfam$fam_mean[data_strategistsfam$strat=='chunks']);
t.test(data_strategistsfam$fam_mean[data_strategistsfam$strat=='chunks'],mu=0.50);
# significantly positively correlated

summary(data_strategistsfam$fam_mean[data_strategistsfam$strat=='intuition']);
t.test(data_strategistsfam$fam_mean[data_strategistsfam$strat=='intuition'],mu=0.50);
# significantly positively correlated

par(mar=c(5,5,2,2));
boxplot(data_strategistsfam$fam_mean~data_strategistsfam$strat,ylab = "Familiarity score",xlab="Testing strategy",ylim=c(0.28,0.9),cex.lab=2,cex.axis=1.75,yaxs="i");
abline(h=0.5, lty=5);
par(mar=c(5, 4, 4, 2) + 0.1); # back to default
```

# BLP

```{r}
data_all_BLP <- read.csv("exp2_BLP_preprocessed.csv",header=T,sep=",");
data_all_BLP <- subset(data_all_BLP, select = -c(X)); # remove redundant column added by Pavlovia
data_BLP <- data_all_BLP[data_all_BLP$sbj_ID %in% participants,]; # n = 190 participants
data_BLP <- data_BLP[!data_BLP$sbj_ID %in% c('667d631ef036f8ef4ff2f4f3','6488afe97766c9083ffc3171','666f0fb7d9900bb03f5d99a1','660310c1b1a7ea09dee682e2','5faacca24cd0384c1fa08be1', '65f7be6ac59662b24ac0f9b0', '664b7cd6b5a772dd1eddca37'),];

BLP_correction <- function(data_BLP)
{
  data_BLP[data_BLP == "polish"] <- "Polish";
  data_BLP[data_BLP == "english"|data_BLP=="English "|data_BLP=="ENGLISH"|data_BLP=="Englsih"|data_BLP=="Englsh"|data_BLP=="British"|data_BLP=="Engllish"|data_BLP=="ENGLISH "] <- "English";
  data_BLP[data_BLP == "portuguese"|data_BLP=="Potuguese"] <- "Portuguese";
  data_BLP[data_BLP =="SPANISH"|data_BLP=="Spnsh"|data_BLP=="spanish"] <- "Spanish";
  data_BLP[data_BLP == "ITALIAN"|data_BLP=="italian"] <- "Italian";
  data_BLP[data_BLP == "sotho"] <- "Sotho";
  data_BLP[data_BLP == "Gree"|data_BLP=="GREEK"] <- "Greek";
  data_BLP[data_BLP == "tshivenda"] <- "Tshivenda";
  data_BLP[data_BLP == "Gujrau"] <- "Gujarati"; # to check
  data_BLP[data_BLP == "ukrainian"|data_BLP=="ukranian"] <- "Ukrainian";
  data_BLP[data_BLP == "SETSWANA"] <- "Setswana";
  data_BLP[data_BLP == "afrikaans"] <- "Afrikaans";
  data_BLP[data_BLP == "punjabi"] <- "Punjabi";
  data_BLP[data_BLP == "siswati"] <- "Siswati";
  data_BLP[data_BLP == "Germany"|data_BLP=="german"|data_BLP=="germany"|data_BLP=="GERMANY"] <- "German";
  data_BLP[data_BLP == "russian"] <- "Russian";
  data_BLP[data_BLP == "Isiulu"] <- "IsiZulu";
  data_BLP[data_BLP == "ZULU"|data_BLP=="zulu"] <- "Zulu";
  data_BLP[data_BLP == "northern sotho"] <- "Northern Sotho";
  data_BLP[data_BLP == "chinese"] <- "Chinese";
  data_BLP[data_BLP == "sesotho"] <- "Sesotho";
  data_BLP[data_BLP == "sepedi"] <- "Sepedi";
  data_BLP[data_BLP == "TSHIVENDA"] <- "Tshivenda";
  data_BLP[data_BLP == "XHOSA"] <- "Xhosa";
  data_BLP[data_BLP == "french"] <- "French";
  data_BLP[data_BLP == "hungarian"] <- "Hungarian";
  data_BLP[data_BLP == "POLISH"] <- "Polish";
  data_BLP[data_BLP == "croatian"] <- "Croatian";
  data_BLP[data_BLP == "bosnian"] <- "Bosnian";
  data_BLP[data_BLP == "madarin"] <- "Mandarin";
  data_BLP[data_BLP == "Icelandic and German"] <- "Icelandic";
  data_BLP[data_BLP == "a little bit of russian"] <- "Russian";
  data_BLP[data_BLP == "NDEBELE"] <- "Ndebele";
  data_BLP[data_BLP == "urdu"] <- "Urdu";
  data_BLP[data_BLP == "latvian"] <- "Latvian";
  data_BLP[data_BLP == "Malayam"] <- "Malayan";
  data_BLP[data_BLP == "swahili"] <- "Swahili";
  data_BLP[data_BLP == "serbian"] <- "Serbian";
  data_BLP[data_BLP == "SEPEDI"] <- "Sepedi";
  data_BLP[data_BLP == "japanese"] <- "Japanese";
  data_BLP[data_BLP == "N/A"|data_BLP=="---"] <- "n/a";
  data_BLP["L1"][is.na(data_BLP["L1"])] <- "n/a";
  data_BLP["L2"][is.na(data_BLP["L2"])] <- "n/a";
  data_BLP["L3"][is.na(data_BLP["L3"])] <- "n/a";
  data_BLP["L4"][is.na(data_BLP["L4"])] <- "n/a";
  
  # correcting some participants' demographic information - correction based off of Prolific's information
  data_BLP["Age"][data_BLP["sbj_ID"] == "60c4a402716a8f9074fcd92e"] <- "21";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6103cbc5310ffddfafa01661"] <- "25";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6598994f0e7e5db183bfe3ee"] <- "23";
  data_BLP["Age"][data_BLP["sbj_ID"] == "66168e55cb60649609600268"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "579e18fc4a84da00014c6f4f"] <- "23";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5c1a6bd8f9250d0001b7c589"] <- "24";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5f6f3d061214fe49ec2b9619"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "60ca0b60979a23c83652c303"] <- "24";
  data_BLP["Age"][data_BLP["sbj_ID"] == "653fb764c9aed77c01457531"] <- "20";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6557def45fc0ffbd46ad01de"] <- "18";
  data_BLP["Age"][data_BLP["sbj_ID"] == "657bfe6e245848c8fef0b389"] <- "20";
  data_BLP["Age"][data_BLP["sbj_ID"] == "65abe33e1c79ea32da32ab0f"] <- "19";
  data_BLP["Age"][data_BLP["sbj_ID"] == "65f33b94cd6885d54029582d"] <- "23";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6634e4d4f1950b4dcd44d4d9"] <- "19";
  data_BLP["Age"][data_BLP["sbj_ID"] == "664b7cd6b5a772dd1eddca37"] <- "25";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6659ca4701d47b95a09ba736"] <- "19";
  data_BLP["Age"][data_BLP["sbj_ID"] == "667dd7126e7a9073e0af73fd"] <- "23";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6681625ff9dfa8a95bb0359d"] <- "21";
  
  return (data_BLP)
};

data_BLP <- BLP_correction(data_BLP);

# make some variables factors
data_BLP$task <- as.factor(data_BLP$task)
data_BLP$sbj_ID <- as.factor(data_BLP$sbj_ID);
data_BLP$Age <- as.numeric(data_BLP$Age);
data_BLP$Gender <- as.factor(data_BLP$Gender);
data_BLP$Education <- as.factor(data_BLP$Education);
data_BLP$L1 <- as.factor(data_BLP$L1);
data_BLP$L2 <- as.factor(data_BLP$L2);
data_BLP$L3 <- as.factor(data_BLP$L3);
data_BLP$L4 <- as.factor(data_BLP$L4);
data_BLP$otherLs <- as.factor(data_BLP$otherLs);
data_BLP$AttentionL1 <- as.factor(data_BLP$AttentionL1);
data_BLP$AttentionL2 <- as.factor(data_BLP$AttentionL2);
data_BLP$AttentionL3 <- as.factor(data_BLP$AttentionL3);
data_BLP$AttentionL4 <- as.factor(data_BLP$AttentionL4);
summary(data_BLP);
# 93/91 M/F split
# mean age = 22.22
# Eng top L1 & L2 lang
```

## PCA

```{r}
scores_list <- subset(data_BLP, select=c('sbj_ID','L1Score','L2Score','L3Score','L4Score')); # combine scores into 1 list
write.csv(scores_list,"BASL_exp2_scores.csv", row.names = FALSE);
use_scores_list <- subset(data_BLP, select=c('sbj_ID','UseL1Score','UseL2Score','UseL3Score','UseL4Score')); # combine use scores into 1 list
write.csv(use_scores_list,"BASL_exp2_usescores.csv", row.names = FALSE);
```

```{r}
# correlations of BLP scores
BLP_scores <- subset(data_BLP,select=c(HistoryL1Score,HistoryL2Score,HistoryL3Score,HistoryL4Score,
                                   UseL1Score,UseL2Score,UseL3Score,UseL4Score,
                                   ProficiencyL1Score,ProficiencyL2Score,ProficiencyL3Score,ProficiencyL4Score,
                                   AttitudeL1Score,AttitudeL2Score,AttitudeL3Score,AttitudeL4Score));
```

```{r}
png('exp2_corrPlot_BLP.png', width=1000, height=1000);
corrplot::corrplot(cor(BLP_scores),type="lower", order="original", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp2_corrPlot_BLP.png"));
```

```{r}
png('exp2_corrPlot_BLP_hclust.png', width=1000, height=1000);
corrplot::corrplot(cor(BLP_scores),type="lower", order="hclust", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp2_corrPlot_BLP_hclust.png"));
```

```{r}
# BLP scores PCA
pca_varimax <- psych::principal(BLP_scores, nfactors=16, rotate='varimax');
data_BLP <- cbind(data_BLP, pca_varimax$scores[,c('RC1','RC3','RC2','RC7','RC9')]);
colnames(data_BLP)[which(names(data_BLP) == "RC1")] <- "RC1_L4";
colnames(data_BLP)[which(names(data_BLP) == "RC3")] <- "RC3_L3";
colnames(data_BLP)[which(names(data_BLP) == "RC2")] <- "RC2_use_L1vsL2";
colnames(data_BLP)[which(names(data_BLP) == "RC7")] <- "RC7_hist_L2";
colnames(data_BLP)[which(names(data_BLP) == "RC9")] <- "RC9_use_L4";
```

```{r}
# scree plot
scree_data <- data.frame(Component = 1:16,Variance = pca_varimax$values[1:16]);
ggplot(scree_data, aes(x = Component, y = Variance)) +
  geom_line(linewidth=1) +
  geom_point(size=4) +
  labs(title = "Scree Plot", x = "Principal Components", y = "Variance Explained") +
  scale_x_discrete(limits=c(seq(from=1,to=16))) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

```{r}
# biplot of 1st 2 PCs
#biplot(pca_varimax, main="Biplot of First Two Principal Components");
```

```{r}
# loadings plot for 1st 2 PCs
loadings_data <- as.data.frame(pca_varimax$loadings[1:16, ]);
loadings_data$BLP_var <- c("L1 History","L2 History", "L3 History", "L4 History",
                       "L1 Use","L2 Use","L3 Use","L4 Use",
                       "L1 Proficiency","L2 Proficiency","L3 Proficiency","L4 Proficiency",
                       "L1 Attitude","L2 Attitude","L3 Attitude","L4 Attitude");
loadings_data$lang <- c(rep(c("L1","L2","L3","L4"),times=4));
ggplot(loadings_data, aes(x=RC1, y=RC3)) +
  geom_point(size=4,colour=c(rep(c(cols2[100],cols2[310],cols2[200],cols2[285]),times=4))) +
  geom_text_repel(aes(label=rownames(loadings_data)),vjust=2,family="CMU Serif",
            position=position_dodge(width=0.01),force=2,size=10,
            colour=c(rep(c(cols2[100],cols2[310],cols2[200],cols2[285]),times=4))) +
  labs(title="PCA Loadings Plot (PC1 vs PC3)",x="PC1 (L4)",y="PC3 (L3)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),legend.position="none",
        legend.background=element_rect(fill=NA));
```

```{r}
# PC1
ggplot(loadings_data, aes(x=BLP_var, y=RC1, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC1 - L4)",y="PC1 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# PC3
ggplot(loadings_data, aes(x=BLP_var, y=RC3, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC3 - L3)",y="PC3 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# PC2
ggplot(loadings_data, aes(x=BLP_var, y=RC2, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC2 - L1 Use vs L2 Use)",y="PC2 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# PC7
ggplot(loadings_data, aes(x=BLP_var, y=RC7, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC7 - L2 History)",y="PC7 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# PC9
ggplot(loadings_data, aes(x=BLP_var, y=RC9, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC9 - L4 Use)",y="PC9 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}

```

```{# Cluster plot of 1st 2 PCs}
cluster_data <- data.frame(pca_varimax$scores[, 1:2]);
colnames(cluster_data) <- c("PC1", "PC2");
ggplot(cluster_data, aes(x = PC1, y = PC2)) +
  geom_point() +
  labs(title = "PCA Cluster Plot (First Two PCs)", x = "Principal Component 1", y = "Principal Component 2") +
  theme_minimal();
```

## Multilingual Metrics

```{r}
multilingual_metrics <- data.frame();
for (i in 1:184) {
  temp <- scores_list[which(scores_list$sbj_ID==unique(scores_list$sbj_ID)[i]),];
  sbj_ID <- temp$sbj_ID[1];
  temp_scores <- as.list(temp);
  temp_scores <- temp_scores[-1];
  temp_scores <- unlist(temp_scores);
  
  use_temp <- use_scores_list[which(use_scores_list$sbj_ID==unique(use_scores_list$sbj_ID)[i]),];
  use_temp_scores <- as.list(use_temp);
  use_temp_scores <- use_temp_scores[-1];
  use_temp_scores <- unlist(use_temp_scores);
  
  # variance
  variance <- var(temp_scores,na.rm=TRUE);
  
  # entropy
  entropy <- Entropy(temp_scores,na.rm=TRUE);
  use_entropy <- Entropy(use_temp_scores,na.rm=TRUE);
  
  # multilingual experience
  multiexp <- sum(temp_scores);
  
  # L1 - L2 score
  L1L2 <- abs(temp_scores[[1]]-temp_scores[[2]]);
  
  multilingual_metrics <- rbind(multilingual_metrics, 
      list(sbj_ID,variance,entropy,use_entropy,multiexp,L1L2));
};
names(multilingual_metrics) <- c("sbj_ID","var","ent","use_ent","multiexp","L1_L2_diff");
data_BLP <- merge(data_BLP,multilingual_metrics,by="sbj_ID");
```

### Cosine Similarity

```{r}
cossim <- read.csv("distances_exp2_NOLOWSCORES.csv",header=T,sep=",");
cossim <- subset(cossim, select = -c(X)); # remove redundant column added by Python
names(cossim) <- c('sbj_ID','cossim');
data_BLP <- merge(data_BLP,cossim,by="sbj_ID");

use_cossim <- read.csv("distances_exp2_usescores.csv",header=T,sep=",");
use_cossim <- subset(use_cossim, select = -c(X)); # remove redundant column added by Python
names(use_cossim) <- c('sbj_ID','use_cossim');
data_BLP <- merge(data_BLP,use_cossim,by="sbj_ID");
```

### Multilingual Category

```{r}
data_BLP$category <- "mono";
data_BLP$category[data_BLP$L2Score>0] <- "bi";
data_BLP$category[data_BLP$L3Score>0] <- "tri";
data_BLP$category[data_BLP$L4Score>0] <- "quadri";
data_BLP$category <- factor(data_BLP$category,levels=c("mono","bi","tri","quadri"));
summary(data_BLP$category);
```

### Script

```{r}
diff_script_sbjID <- c('5e8b85a61e16e9057a996e36','60c715c89bb47f3847a690f0','655f8b959477c803eb906622','65a97afe116a650acc588c5b','65cba84263ac644fa79702ca','65fae6b84fa6b3101d2ca4b1','66031000461c44484ac359a8','66271b4aaaf60fd058302f09','6667488c5f46f3da0c085419','667972671949d2e1c0c9ff54');
# n=10
mixed_script_sbjID <- c('5ebd8f8679146d0a116bc257','5eff8b9ad19111064484eff7','5f5a5d4618746310515e2828','6057a8fe2d302939fc759940','60907b8091341e8724ba80ed','60f9739250a5c6f6e4726336','6106ac34408681f3b0d07396','61242dd5be1a06b174975a1f','6492c23a1a7735dfaab2b095','64e9d6f596308448ac67bb95','650330fa0cbc534b423f41e9','65352001dbe3e18eae5a8300','65672c69a3737224f1d0bbfa','65a97217d4fb858939a16b0f','65dce7715387badaf80e875d','660c265dce47171c0dd7d359','663a5bb8f7f79c7e04abc9b3','668992b2f868cb89829346c2');
# n=18
sbj_IDs_included <- list(unique(data_BLP$sbj_ID))[[1]];
same_script_sbjID <- sbj_IDs_included[!sbj_IDs_included %in% diff_script_sbjID];
same_script_sbjID <- same_script_sbjID[!same_script_sbjID %in% mixed_script_sbjID];
# n=156
data_BLP$script[data_BLP$sbj_ID %in% diff_script_sbjID] <- 'mixed/diff';
data_BLP$script[data_BLP$sbj_ID %in% mixed_script_sbjID] <- 'mixed/diff';
data_BLP$script[data_BLP$sbj_ID %in% same_script_sbjID] <- 'same';
data_BLP$script <- factor(data_BLP$script,levels=c("same","mixed/diff"));
```

### Metric Comparisons

```{r}
#var
summary(data_BLP$var);
var(data_BLP$var);
```

```{r}
#ent
summary(data_BLP$ent);
var(data_BLP$ent);

cor.test(data_BLP$var,data_BLP$ent,method="pearson"); 
# significantly very strongly negatively correlated 

ggplot(data_BLP, aes(x=sbj_ID,y=ent,colour=category)) +
  geom_point(size=4) +
  labs(x = "Participant ID", y = "Multilingual balance (entropy)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        axis.text.x=element_blank(),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.15,0.25),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual","Bilingual","Trilingual","Quadrilingual"));

hist(data_BLP$ent,breaks=1000,xlab="Multilingual balance (entropy)",
     main="",cex.lab=2,cex.axis=1.5);
# lots at 0 and 1
```

```{r}
#use_ent
summary(data_BLP$use_ent);
var(data_BLP$use_ent);
```

```{r}
#multiexp
summary(data_BLP$multiexp);
var(data_BLP$multiexp);
```

```{r}
#L1_L2_diff
summary(data_BLP$L1_L2_diff);
var(data_BLP$L1_L2_diff);
```

```{r}
#cossim
summary(data_BLP$cossim);
var(data_BLP$cossim);

ggplot(data_BLP, aes(x=sbj_ID,y=cossim,colour=category)) +
  geom_point(size=4) +
  labs(x = "Participant ID", y = "Multilingual balance (cosine similarity)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        axis.text.x=element_blank(),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.15,0.15),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual","Bilingual","Trilingual","Quadrilingual"));

hist(data_BLP$cossim,breaks=1000,
     xlab="Multilingual balance (cosine similarity)",main="",
     cex.lab=2,cex.axis=1.5);
# lots at 1
hist(data_BLP$cossim[data_BLP$category!="mono"],breaks=1000,
     xlab="Multilingual balance (cosine similarity)",main="",
     cex.lab=2,cex.axis=1.5);
# exponential distribution
```

```{r}
ggplot(data_BLP, aes(x=cossim,y=ent,colour=category)) +
  geom_point(size=4) +
  labs(x = "Multilingual balance (cosine similarity)", y = "Multilingual balance (entropy)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.17,0.2),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual (n=22)","Bilingual (n=70)",
                              "Trilingual (n=51)","Quadrilingual (n=41)"));
```

```{r}
#use_cossim
summary(data_BLP$use_cossim);
var(data_BLP$use_cossim);

# cossim & use_cossim
cor.test(data_BLP$cossim,data_BLP$use_cossim,method="pearson");
# significantly strongly positively correlated
```

```{r}
#ent & multiexp
cor.test(data_BLP$ent,data_BLP$multiexp,method="pearson");
# significantly very strongly positively correlated

ggplot(data_BLP, aes(x=multiexp,y=ent,colour=category)) +
  geom_point(size=4) +
  labs(x = "Multilingual experience", y = "Multilingual balance (entropy)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.8,0.2),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual (n=22)","Bilingual (n=70)",
                              "Trilingual (n=51)","Quadrilingual (n=41)"));
```

```{r}
#cossim & multiexp
cor.test(data_BLP$cossim,data_BLP$multiexp,method="pearson");
# not significant

ggplot(data_BLP, aes(x=cossim,y=multiexp,colour=category)) +
  geom_point(size=4) +
  labs(y = "Multilingual experience", x = "Multilingual balance (entropy)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.17,0.8),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual (n=22)","Bilingual (n=70)",
                              "Trilingual (n=51)","Quadrilingual (n=41)"));
```

```{r}
#cossim & ent
cor.test(data_BLP$cossim,data_BLP$ent,method="pearson");
# no monos:
cor.test(data_BLP$cossim[data_BLP$category!="mono"],data_BLP$ent[data_BLP$category!="mono"],method="pearson");
# no corr
```

```{r}
#ent & use_ent
cor.test(data_BLP$ent,data_BLP$use_ent,method="pearson");
# significantly strongly positively correlated
```

```{r}
# correlations of multilingual metrics
M <- cor(subset(data_BLP,select=c('var','ent','use_ent','multiexp','L1_L2_diff','cossim','use_cossim')));
png('exp2_corrPlot_multimetrics.png', width=1000, height=1000);
corrplot::corrplot(M,type="lower", order="original", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',number.cex=1.5,tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp2_corrPlot_multimetrics.png"));
```

```{r}
png('exp2_corrPlot_multimetrics_hclust.png', width=1000, height=1000);
corrplot::corrplot(M,type="lower", order="hclust", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black', number.cex=1.5,tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp2_corrPlot_multimetrics_hclust.png"));
```

```{r}
# export BLP dataframe
write.csv(data_BLP,"BASL_exp2_BLP.csv", row.names = FALSE);
```

```{r}
# combining BLP & testing scores
data_BLP_shortened <- subset(data_BLP, select=c(sbj_ID,Gender,Age,
                                                HistoryL1Score,HistoryL2Score,HistoryL3Score,HistoryL4Score,
                                                UseL1Score,UseL2Score,UseL3Score,UseL4Score,
                                                ProficiencyL1Score,ProficiencyL2Score,ProficiencyL3Score,ProficiencyL4Score,
                                                AttitudeL1Score,AttitudeL2Score,AttitudeL3Score,AttitudeL4Score,
                                                L1Score,L2Score,L3Score,L4Score,
                                                var,ent,use_ent,multiexp,L1_L2_diff,cossim,use_cossim,
                                                RC1_L4,RC3_L3,RC2_use_L1vsL2,RC7_hist_L2,RC9_use_L4,
                                                category,script));
data_BLP_testing <- list(data_testing,data_BLP_shortened) %>% reduce(inner_join, by='sbj_ID');
data_BLP_familiarity <- list(data_familiarity,data_BLP_shortened) %>% reduce(inner_join, by='sbj_ID');
```

```{r}
# correlations of BLP metrics with testing scores
M <- cor(subset(data_BLP_testing,select=c(score_2M,dprime,c,
                                          var,ent,use_ent,multiexp,L1_L2_diff,cossim,use_cossim,
                                          RC1_L4,RC3_L3,RC2_use_L1vsL2,RC7_hist_L2,RC9_use_L4)));
png('exp2_corrPlot_BLP_testing.png', width=1000, height=1000);
corrplot::corrplot(M,type="lower", order="original", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp2_corrPlot_BLP_testing.png"));
```

```{r}
png('exp2_corrPlot_BLP_testing_hclust.png', width=1000, height=1000);
corrplot::corrplot(M,type="lower", order="hclust", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp2_corrPlot_BLP_testing_hclust.png"));
```

```{r}
# export BLP testing dataframe
write.csv(data_BLP_testing,"BASL_exp2_BLPtesting.csv", row.names = FALSE);
```

# LINEAR MODELLING

## "Yes" Responses LMERs

### Testing Conditions

```{r}
lm_TestingConditions <- glmer(observed ~ scale(trialn) + testing_condition + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_TestingConditions);
effect_conditions <- as.data.frame(effect('testing_condition',
                                          lm_TestingConditions, confint=list(alpha=.95)),
                                   xlevels = list(testing_condition=c('0M','1M','2M')));
effect_conditions
export_output(model=lm_TestingConditions,name="Exp. 2 `Yes' responses - Conditions",
              pred_levels=c('0M','1M','2M'),pred_type='categorical',
              outcome_levels=c('0M','1M','2M'));
```

### Gender

```{r}
lm_Gender <- glmer(observed ~ scale(trialn) + testing_condition*Gender + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_Gender);
export_output(model=lm_Gender,name="Exp. 2 `Yes' responses - Gender",
              pred_levels=c('Man','Woman'),pred_type='categorical',
              outcome_levels=c('0M','1M','2M'));
```

### Age

```{r}
lm_Age <- glmer(observed ~ scale(trialn) + testing_condition*scale(Age) + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_Age);
export_output(model=lm_Age,name="Exp. 2 `Yes' responses - Age",
              pred_levels=c('scale(Age)'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC1

```{r}
lm_RC1 <- glmer(observed ~ scale(trialn) + testing_condition*RC1_L4 + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC1);
export_output(model=lm_RC1,name="Exp. 2 `Yes' responses - PC1 (L4)",
              pred_levels=c('PC1_L4'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC3

```{r}
lm_RC3 <- glmer(observed ~ scale(trialn) + testing_condition*RC3_L3 + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC3);
export_output(model=lm_RC3,name="Exp. 2 `Yes' responses - PC3 (L3)",
              pred_levels=c('PC3_L3'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC2

```{r}
lm_RC2 <- glmer(observed ~ scale(trialn) + testing_condition*RC2_use_L1vsL2 + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC2);
export_output(model=lm_RC2,name="Exp. 2 `Yes' responses - PC2 (L1 vs L2 Use)",
              pred_levels=c('PC2_L1vsL2_Use'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC7

```{r}
lm_RC7 <- glmer(observed ~ scale(trialn) + testing_condition*RC7_hist_L2 + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC7);
export_output(model=lm_RC7,name="Exp. 2 `Yes' responses - PC7 (L2 History)",
              pred_levels=c('PC7_L2_History'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC9

```{r}
lm_RC9 <- glmer(observed ~ scale(trialn) + testing_condition*RC9_use_L4 + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC9);
export_output(model=lm_RC9,name="Exp. 2 `Yes' responses - PC9 (L4 Use)",
              pred_levels=c('PC9_L4_Use'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### Entropy

```{r}
lm_ent <- glmer(observed ~ testing_condition*ent + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_ent);
export_output(model=lm_ent,name="Exp. 2 `Yes' responses - Multilingual balance (Entropy)",
              pred_levels=c('Entropy'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### Use Entropy

```{r}
lm_use_ent <- glmer(observed ~ testing_condition*use_ent + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_use_ent);
```

### Multilingual Experience

```{r}
lm_multiexp <- glmer(observed ~ scale(trialn) + testing_condition*scale(multiexp) + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_multiexp);
export_output(model=lm_multiexp,name="Exp. 2 `Yes' responses - Multilingual experience",
              pred_levels=c('scale(Multilingual experience)'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### L1-L2 Difference

```{r}
lm_L1L2diff <- glmer(observed ~ scale(trialn) + testing_condition*scale(L1_L2_diff) + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_L1L2diff);
export_output(model=lm_L1L2diff,name="Exp. 2 `Yes' responses - Bilingual balance (L1-L2 difference)",
              pred_levels=c('scale(L1-L2 difference)'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### Cosine Similarity

```{r}
lm_cossim <- glmer(observed ~ testing_condition*cossim + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial',control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)));
summary(lm_cossim);
export_output(model=lm_cossim,name="Exp. 2 `Yes' responses - Multilingual balance (cosine similarity)",
              pred_levels=c('Cosine similarity'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

```{r}
lm_cossim_nomonos <- glmer(observed ~ testing_condition*cossim + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000 & category != "mono"), family='binomial',control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)));
summary(lm_cossim_nomonos);
```

### Use Cosine Similarity

```{r}
lm_use_cossim <- glmer(observed ~ testing_condition*use_cossim + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial',control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)));
summary(lm_use_cossim);
```

### Script

```{r}
lm_script <- glmer(observed ~ testing_condition*script + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_script);
export_output(model=lm_script,name="Exp. 2 `Yes' responses - Script",
              pred_levels=c('Same script','Different script'),pred_type='categorical',
              outcome_levels=c('0M','1M','2M'));
```

### Category

```{r}
lm_category <- glmer(observed ~ testing_condition*category + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial',control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)));
summary(lm_category);
export_output(model=lm_category,name="Exp. 2 `Yes' responses - Category",
              pred_levels=c('Monolingual','Bilingual','Trilingual','Quadrilingual'),
              pred_type='categorical',
              outcome_levels=c('0M','1M','2M'));
```

## 2M Responses LMERs

```{r}
lm_2M <- glmer(observed ~ scale(trialn) + expected + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M);
effect_2M <- as.data.frame(effect('expected',lm_2M,confint=list(alpha=.95)),
                           xlevels = list(expected=c(0,1)));
export_output(model=lm_2M,name="Exp. 2 2M",
              pred_levels=c('between_language','within_language'),
              pred_type='categorical',
              outcome_levels=c('between_language','within_language'));
```

### Gender

```{r}
lm_2M_Gender <- glmer(observed ~ scale(trialn) + expected*Gender + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_Gender);
export_output(model=lm_2M_Gender,name="Exp. 2 2M - Gender",
              pred_levels=c('Man','Woman'),pred_type='categorical',
              outcome_levels=c('between_language','within_language'));
```

### Age

```{r}
lm_2M_Age <- glmer(observed ~ scale(trialn) + expected*scale(Age) + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_Age);
export_output(model=lm_2M_Age,name="Exp. 2 2M - Age",
              pred_levels=c('scale(Age)'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC1

```{r}
lm_2M_RC1 <- glmer(observed ~ scale(trialn) + expected*RC1_L4 + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC1);
export_output(model=lm_2M_RC1,name="Exp. 2 2M - PC1 (L4)",
              pred_levels=c('PC1_L4'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC3

```{r}
lm_2M_RC3 <- glmer(observed ~ scale(trialn) + expected*RC3_L3 + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC3);
export_output(model=lm_2M_RC3,name="Exp. 2 2M - PC3 (L3)",
              pred_levels=c('PC3_L3'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC2

```{r}
lm_2M_RC2 <- glmer(observed ~ scale(trialn) + expected*RC2_use_L1vsL2 + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC2);
export_output(model=lm_2M_RC2,name="Exp. 2 2M - PC2 (L1 vs L2 Use)",
              pred_levels=c('PC2_L1vsL2_Use'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC7

```{r}
lm_2M_RC7 <- glmer(observed ~ scale(trialn) + expected*RC7_hist_L2 + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC7);
export_output(model=lm_2M_RC7,name="Exp. 2 2M - PC7 (L2 History)",
              pred_levels=c('PC7_L2_History'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC9

```{r}
lm_2M_RC9 <- glmer(observed ~ scale(trialn) + expected*RC9_use_L4 + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC9);
export_output(model=lm_2M_RC9,name="Exp. 2 2M - PC9 (L4 Use)",
              pred_levels=c('PC9_L4_Use'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### Entropy

```{r}
lm_2M_ent <- glmer(observed ~ scale(trialn) + expected*ent + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_ent);
export_output(model=lm_2M_ent,name="Exp. 2 2M - Multilingual balance (Entropy)",
              pred_levels=c('Entropy'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### Use Entropy

```{r}
lm_2M_use_ent <- glmer(observed ~ scale(trialn) + expected*use_ent + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_use_ent);
```

### Multilingual Experience

```{r}
lm_2M_multiexp <- glmer(observed ~ scale(trialn) + expected*scale(multiexp) + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_multiexp);
export_output(model=lm_2M_multiexp,name="Exp. 2 2M - Multilingual experience",
              pred_levels=c('scale(Multilingual experience)'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### L1-L2 Difference

```{r}
lm_2M_L1L2diff <- glmer(observed ~ scale(trialn) + expected*scale(L1_L2_diff) + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_L1L2diff);
export_output(model=lm_2M_L1L2diff,name="Exp. 2 2M - Bilingual Balance (L1-L2 difference)",
              pred_levels=c('scale(L1-L2 difference)'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### Cosine Similarity

```{r}
lm_2M_cossim <- glmer(observed ~ scale(trialn) + expected*scale(cossim) + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_cossim);
export_output(model=lm_2M_cossim,name="Exp. 2 2M - Multilingual balance (cosine similarity)",
              pred_levels=c('scale(Cosine similarity)'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

```{r}
lm_2M_cossim_nomonos <- glmer(observed ~ scale(trialn) + expected*scale(cossim) + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000&data_BLP_testing$category!='mono',], family='binomial');
summary(lm_2M_cossim_nomonos);
```

### Use Cosine Similarity

```{r}
lm_2M_use_cossim <- glmer(observed ~ scale(trialn) + expected*scale(use_cossim) + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_use_cossim);
```

### Script

```{r}
lm_2M_script <- glmer(observed ~ scale(trialn) + expected*script + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_script);
export_output(model=lm_2M_script,name="Exp. 2 2M - Script",
              pred_levels=c('Same script','Different script'),pred_type='categorical',
              outcome_levels=c('between_language','within_language'));

plot_model(lm_2M_script,type = 'pred', terms = c('expected', 'script'));
```

### Category

```{r}
lm_2M_category <- glmer(observed ~ scale(trialn) + expected*category + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M' & data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_category);
export_output(model=lm_2M_category,name="Exp. 2 2M - Category",
              pred_levels=c('Monolingual','Bilingual','Trilingual','Quadrilingual'),
              pred_type='categorical',
              outcome_levels=c('between_language','within_language'));

plot_model(lm_2M_category,type = 'pred', terms = c('expected', 'category'));
```

## Familiarity Responses LMERs

```{r}
data_BLP_familiarity$correct_numerical <- as.numeric(data_BLP_familiarity$correct);
```

### Gender

```{r}
lm_fam_Gender <- glmer(correct ~ scale(trialn) + Gender + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_Gender);
export_output(model=lm_fam_Gender,name="Exp. 2 Familiarity - Gender",
              pred_levels=c('Man','Woman'),pred_type='categorical',
              outcome_levels=c('wrong','right'));
```

### Age

```{r}
lm_fam_Age <- glmer(correct ~ scale(trialn) + scale(Age) + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_Age);
export_output(model=lm_fam_Age,name="Exp. 2 Familiarity - Age",
              pred_levels=c('scale(Age)'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC1

```{r}
lm_fam_RC1 <- glmer(correct ~ scale(trialn) + RC1_L4 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC1);
export_output(model=lm_fam_RC1,name="Exp. 2 Familiarity - PC1 (L4)",
              pred_levels=c('PC1_L4'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC3

```{r}
lm_fam_RC3 <- glmer(correct ~ scale(trialn) + RC3_L3 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC3);
export_output(model=lm_fam_RC3,name="Exp. 2 Familiarity - PC3 (L3)",
              pred_levels=c('PC3_L3'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC2

```{r}
lm_fam_RC2 <- glmer(correct ~ scale(trialn) + RC2_use_L1vsL2 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC2);
export_output(model=lm_fam_RC2,name="Exp. 2 Familiarity - PC2 (L1 vs L2 Use)",
              pred_levels=c('PC2_L1vsL2_Use'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC7

```{r}
lm_fam_RC7 <- glmer(correct ~ scale(trialn) + RC7_hist_L2 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC7);
export_output(model=lm_fam_RC7,name="Exp. 2 Familiarity - PC7 (L2 History)",
              pred_levels=c('PC7_L2_History'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC9

```{r}
lm_fam_RC9 <- glmer(correct ~ scale(trialn) + RC9_use_L4 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC9);
export_output(model=lm_fam_RC9,name="Exp. 2 Familiarity - PC9 (L4 Use)",
              pred_levels=c('PC4_L4_Use'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### Entropy

```{r}
lm_fam_ent <- glmer(correct ~ scale(trialn) + ent + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_ent);
export_output(model=lm_fam_ent,name="Exp. 2 Familiarity - Multilingual balance (entropy)",
              pred_levels=c('Entropy'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### Use Entropy

```{r}
lm_fam_use_ent <- glmer(correct ~ scale(trialn) + use_ent + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_use_ent);
```

### Multilingual Experience

```{r}
lm_fam_multiexp <- glmer(correct ~ scale(trialn) + scale(multiexp) + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_multiexp);
export_output(model=lm_fam_multiexp,name="Exp. 2 Familiarity - Multilingual experience",
              pred_levels=c('scale(Multilingual experience)'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### L1-L2 Difference

```{r}
lm_fam_L1L2diff <- glmer(correct ~ scale(trialn) + scale(L1_L2_diff) + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_L1L2diff);
export_output(model=lm_fam_L1L2diff,name="Exp. 2 Familiarity - Bilingual balance (L1-L2 difference)",
              pred_levels=c('scale(L1-L2 difference)'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### Cosine Similarity

```{r}
lm_fam_cossim <- glmer(correct ~ scale(trialn) + cossim + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_cossim);
export_output(model=lm_fam_cossim,name="Exp. 2 Familiarity - Multilingual balance (cosine similarity)",
              pred_levels=c('Cosine similarity'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### Use Cosine Similarity

```{r}
lm_fam_use_cossim <- glmer(correct ~ scale(trialn) + use_cossim + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_use_cossim); 
```

### Script

```{r}
lm_fam_script <- glmer(correct ~ scale(trialn) + script + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_script); 
export_output(model=lm_fam_script,name="Exp. 2 Familiarity - Script",
              pred_levels=c('Same script','Different script'),pred_type='categorical',
              outcome_levels=c('wrong','right'));
```

### Category

```{r}
lm_fam_category <- glmer(correct ~ scale(trialn) + category + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_category); 
export_output(model=lm_fam_category,name="Exp. 2 Familiarity - Category",
              pred_levels=c('Monolingual','Bilingual','Trilingual','Quadrilingual'),
              pred_type='categorical',outcome_levels=c('wrong','right'));
```

# EXPLORATION OF SIGNIFICANT EFFECTS

```{r}
data_testing_conditions_BLP <- merge(data_testing_conditions,subset(data_BLP,select=c(sbj_ID,Gender,Age,RC2_use_L1vsL2,RC7_hist_L2,multiexp,L1_L2_diff,script,category)),by="sbj_ID");
```

## "Yes" Responses

### "Yes" - Testing Conditions

```{r}
ggplot(data_testing_conditions, aes(x=condition, y=score, fill=condition)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_violin(alpha=0.75) +
  
  geom_errorbar(aes(x=1,ymin=effect_conditions$lower[[1]],
                    ymax=effect_conditions$upper[[1]]),width=.1) + # 0M
  annotate("point",x=1,y=effect_conditions$fit[[1]],colour=cols2[100],size=2) + # 0M
  
  geom_errorbar(aes(x=2,ymin=effect_conditions$lower[[2]],
                    ymax=effect_conditions$upper[[2]]),width=.1) + # 1M
  annotate("point",x=2,y=effect_conditions$fit[[2]],colour=cols2[200],size=2) + # 1M
  
  geom_errorbar(aes(x=3,ymin=effect_conditions$lower[[3]],
                    ymax=effect_conditions$upper[[3]]),width=.1) + # 2M
  annotate("point",x=3,y=effect_conditions$fit[[3]],colour="#004D40FF",size=2) + # 2M
  
  ylim(0,1.01) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF")) +
  labs(x = "Testing condition", y = 'Proportion of "yes" responses') +
  scale_x_discrete(labels=c("0M", "1M", "2M")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position = "none");
```

### "Yes" - Gender

```{r}
ggplot(data_testing_conditions_BLP, aes(x=condition,y=score,fill=Gender,group=interaction(condition,Gender))) +
  scale_fill_manual(values=c(cols2[400],cols2[310])) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_boxplot(alpha = 0.75, width=0.75) +
  geom_point(position = position_dodge(width=0.75),size=2) +
  labs(x = "Condition", y = 'Proportion of "yes" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.9,0.1),legend.background=element_rect(fill=NA)) +
  ylim(0,1.05) +
  coord_cartesian(expand = FALSE) +
  scale_x_discrete(labels=c("0M", "1M", "2M"));
# Women say "yes" more in 1M
```

### "Yes" - Age

```{r}
effect_Age <- as.data.frame(effect('testing_condition*scale(Age)',
                                   lm_Age, confint=list(alpha=.95)),
                            xlevels = list(Age = 18:25,
                                           testing_condition=c('0M','1M','2M')));

ggplot(effect_Age, aes(x=Age,y=fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  labs(x = "Age", y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.1,0.1),legend.background=element_rect(fill=NA));
# Older -> bigger morph familiarity effect
```

### "Yes" - PC2

```{r}
effect_RC2 <- as.data.frame(effect('testing_condition*RC2_use_L1vsL2',
                                   lm_RC2, confint=list(alpha=.95)),
                            xlevels = list(RC2_use_L1vsL2 = -1.9:3.9,
                                           testing_condition=c('0M','1M','2M')))

ggplot(effect_RC2, aes(x=RC2_use_L1vsL2,y=fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  labs(x = "RC2: L1 vs L2 Use", y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.1,0.9),legend.background=element_rect(fill=NA));
# More L2 use = greater morph fam effect (not overlapping so not 100% sure)
```

### "Yes" - PC7

```{r}
effect_RC7 <- as.data.frame(effect('testing_condition*RC7_hist_L2',
                                   lm_RC7, confint=list(alpha=.95)),
                            xlevels = list(RC7_hist_L2 = -2.1:3.1,
                                           testing_condition=c('0M','1M','2M')));

ggplot(effect_RC7, aes(x=RC7_hist_L2,y=fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  labs(x = "RC7: L2 History", y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.1,0.9),legend.background=element_rect(fill=NA));
# Earlier bilingual = more "yes" responses overall
```

### "Yes" - Multilingual Experience

```{r}
effect_multiexp <- as.data.frame(effect('testing_condition*scale(multiexp)',
                                        lm_multiexp, confint=list(alpha=.95)),
                                 xlevels = list(L1_L2_diff = 154:702,
                                                testing_condition=c('0M','1M','2M')))

ggplot(effect_multiexp, aes(x = multiexp, y = fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.9,0.9),legend.background=element_rect(fill=NA)) +
  labs(x = 'Mulilingual experience', y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4');
# More multiexp = more "yes" responses overall
```

### "Yes" - L1-L2 Difference

```{r}
effect_L1L2diff <- as.data.frame(effect('testing_condition*scale(L1_L2_diff)',
                                        lm_L1L2diff, confint=list(alpha=.95)),
                                 xlevels = list(L1_L2_diff = 0:210,
                                                testing_condition=c('0M','1M','2M')));

ggplot(effect_L1L2diff, aes(x = L1_L2_diff, y = fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.9,0.9),legend.background=element_rect(fill=NA)) +
  labs(x = 'Bilingual balance (L1-L2 difference)', y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4');
# More balanced bi = more sig morph fam effect & 2M "yes" more different from 1M "yes"
```

### "Yes" - Script

```{r}
ggplot(data_testing_conditions_BLP, aes(x=condition,y=score,fill=script,group=interaction(condition,script))) +
  scale_fill_manual(values=c(cols2[400],cols2[310])) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_boxplot(alpha = 0.75, width=0.75) +
  geom_point(position = position_dodge(width=0.75),size=2) +
  labs(x = "Condition", y = 'Proportion of "yes" responses') +
  ylim(0,1.05) +
  coord_cartesian(expand = FALSE) +
  scale_x_discrete(labels=c("0M", "1M", "2M")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.9,0.1),legend.background=element_rect(fill=NA));
# Very slight 1M boxplot for mixed/diff lower... not really anything, especially
# with small mixed/diff sample size
```

## 2M Responses

```{r}
BLP_2Mscores <- data_BLP_testing[!duplicated(data_BLP_testing$sbj_ID), ];

data_testing_2M_aggr <- data_testing_2M_aggr[data_testing_2M_aggr$response=="meanYes",];
```

```{r}
ggplot(data_testing_2M_aggr, aes(x=expected, y=meanValue, fill=expected)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  
  geom_errorbar(aes(x=1,ymin=effect_2M$lower[[1]],ymax=effect_2M$upper[[1]]),
                width=.1) + # false alarm
  annotate("point",x=1,y=effect_2M$fit[[1]],colour="darkred",size=2) + # false alarm
  
  geom_errorbar(aes(x=2,ymin=effect_2M$lower[[2]],ymax=effect_2M$upper[[2]]),
                width=.1) + # hit
  annotate("point",x=2,y=effect_2M$fit[[2]],colour="lightblue",size=2) + # hit
  
  scale_fill_manual(values=c(cols2[100],cols2[200])) +
  scale_x_discrete(labels=c('Between-language', 'Within-language')) +
  labs(x = "String nature", y = 'Proportion of "yes" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="none",legend.background=element_rect(fill=NA));
```

### 2M - L1-L2 Difference

```{r}
ggplot(data_BLP_testing, aes(x=L1_L2_diff,y=yes_2M)) +
  geom_hline(yintercept=50,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "Bilingual balance (L1-L2 difference)", y = 'Percent of 2M "yes" responses') +
  ylim(0,101) + 
  xlim(min(data_BLP_testing$L1_L2_diff)-2,max(data_BLP_testing$L1_L2_diff)+2) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### 2M - Cosine Similarity

```{r}
lm_2M_cossim_nooutlier <- glmer(observed ~ scale(trialn) + expected*scale(cossim) + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000&data_BLP_testing$score_2M>0.25,], family='binomial');
summary(lm_2M_cossim_nooutlier);
# no longer sig when remove participant with lowest 2M score (22.5%)
```

```{r}
ggplot(data_BLP_testing, aes(x=cossim,y=score_2M)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "Multilingual balance (cosine similarity)", y = '2M accuracy') +
  ylim(0,1.1) + 
  xlim(min(data_BLP_testing$cossim)-0.01,max(data_BLP_testing$cossim)+0.01) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

```{r}
# without outlier
ggplot(data_BLP_testing[data_BLP_testing$score_2M>0.25,], aes(x=cossim,y=score_2M)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "Multilingual balance (cosine similarity) - no outlier", y = '2M accuracy') +
  ylim(0,1.1) + 
  xlim(min(data_BLP_testing$cossim)-0.01,max(data_BLP_testing$cossim)+0.01) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

```{r}
plot(data_BLP_testing$yes_2M~data_BLP_testing$cossim,pch=19,ylim=c(0,100),
     xlab="Multilingual balance (cosine similarity)",ylab='Percent of 2M "yes" responses',
     cex.lab=2,cex.axis=1.5);
abline(lm(data_BLP_testing$yes_2M~data_BLP_testing$cossim), col = "red",lwd=2);
abline(h=50,lty=5);
```

### 2M - Entropy

```{r}
ggplot(data_BLP_testing, aes(x=ent,y=score_2M)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "Multilingual balance (entropy)", y = '2M accuracy') +
  ylim(0,1.1) + 
  xlim(min(data_BLP_testing$ent)-0.1,max(data_BLP_testing$ent)+0.1) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### 2M - Script

```{r}
ggplot(data_BLP_testing, aes(x=script,y=score_2M)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_boxplot(fill="darkgrey") +
  labs(x = "Script", y = '2M accuracy') +
  scale_x_discrete(labels=c('Same', 'Different')) +
  ylim(0,1.1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

```{r}
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$script=='same'],mu=0.5);
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$script=='diff/mixed'],mu=0.5);
```

```{r}
data_testing_2M_script_aggr <- data_BLP_testing %>% 
  mutate(correct01 = case_when(correct == TRUE ~ 1,
                               correct == FALSE ~ 0),
         yesno01 = case_when(observed == 'between_lang' ~ 0,
                             observed == 'within_lang' ~ 1)) %>% 
  filter(testing_condition == '2M') %>% 
  group_by(expected, sbj_ID, script) %>% 
  dplyr::summarise(meanCorrect = mean(correct01), se = sd(correct01/sqrt(n())),
                   meanYes = mean(yesno01), se = sd(yesno01/sqrt(n()))) %>% 
  mutate(meanNo = 1 - meanYes);
data_testing_2M_script_aggr <- data_testing_2M_script_aggr %>%
  pivot_longer(
    cols = c(meanYes, meanNo),
    names_to = "response",
    values_to = "meanValue"
  );
```

```{r}
ggplot(data_testing_2M_script_aggr[data_testing_2M_script_aggr$response=="meanYes",], aes(x=expected, y=meanValue, fill=script)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  geom_boxplot(position=position_dodge(width=1),width=0.25) +
  scale_fill_manual(name="Script",labels=c('Same','Different'),values=c(cols2[400],cols2[310])) +
  scale_x_discrete(labels=c('Between-language', 'Within-language')) +
  labs(x = "String nature", y = 'Proportion of "within-language" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),legend.position="inside",
        legend.position.inside=c(0.1,0.1),legend.background=element_rect(fill=NA));
```

### 2M - Category

```{r}
ggplot(BLP_2Mscores, aes(x=category,y=score_2M)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_boxplot(fill="darkgrey") +
  labs(x = "Multilingual category", y = '2M accuracy') +
  scale_x_discrete(labels=c('Monolingual','Bilingual','Trilingual','Quadrilingual')) +
  ylim(0,1.1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

```{r}
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$category=='mono'],mu=0.5);
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$category=='bi'],mu=0.5);
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$category=='tri'],mu=0.5);
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$category=='quadri'],mu=0.5);
```

```{r}
t.test(BLP_2Mscores$dprime[BLP_2Mscores$category=='mono'],mu=0);
t.test(BLP_2Mscores$dprime[BLP_2Mscores$category=='bi'],mu=0);
t.test(BLP_2Mscores$dprime[BLP_2Mscores$category=='tri'],mu=0);
t.test(BLP_2Mscores$dprime[BLP_2Mscores$category=='quadri'],mu=0);
```

```{r}
data_testing_2M_category_aggr <- data_BLP_testing %>% 
  mutate(correct01 = case_when(correct == TRUE ~ 1,
                               correct == FALSE ~ 0),
         yesno01 = case_when(observed == 'between_lang' ~ 0,
                             observed == 'within_lang' ~ 1)) %>% 
  filter(testing_condition == '2M') %>% 
  group_by(expected, sbj_ID, category) %>% 
  dplyr::summarise(meanCorrect = mean(correct01), se = sd(correct01/sqrt(n())),
                   meanYes = mean(yesno01), se = sd(yesno01/sqrt(n()))) %>% 
  mutate(meanNo = 1 - meanYes);
```

```{r}
ggplot(data_testing_2M_category_aggr, aes(x=expected, y=meanCorrect, fill=expected)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  
  geom_errorbar(aes(x=1,ymin=effect_2M$lower[[1]],ymax=effect_2M$upper[[1]]),
                width=.1) + # false alarm
  annotate("point",x=1,y=effect_2M$fit[[1]],colour="darkred",size=2) + # false alarm
  
  geom_errorbar(aes(x=2,ymin=effect_2M$lower[[2]],ymax=effect_2M$upper[[2]]),
                width=.1) + # hit
  annotate("point",x=2,y=effect_2M$fit[[2]],colour="lightblue",size=2) + # hit
  
  scale_fill_manual(values=c(cols2[100],cols2[200])) +
  scale_x_discrete(labels=c('Between-language', 'Within-language')) +
  labs(x = "String nature", y = 'Proportion of "yes" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="none",legend.background=element_rect(fill=NA))+
  facet_wrap(~category);
```

## Familiarity Responses

### Familiarity - PC9

```{r}
ggplot(data_BLP_familiarity, aes(x=RC9_use_L4,y=fam_mean)) +
  geom_hline(yintercept=0.50,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "PC9 (L4 Use)", y = 'Familiarity accuracy') +
  ylim(0,1) + 
  xlim(min(data_BLP_familiarity$RC9_use_L4)-0.1,max(data_BLP_familiarity$RC9_use_L4)+0.1) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

### Familiarity - Entropy

```{r}
BLP_fam <- data_BLP_familiarity[!duplicated(data_BLP_familiarity$sbj_ID), ];
```

```{r}
ggplot(data_BLP_familiarity, aes(x=ent,y=fam_mean)) +
  geom_hline(yintercept=0.50,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "Multilingual balance (entropy)", y = 'Familiarity accuracy') +
  ylim(0,1) + 
  xlim(min(data_BLP_familiarity$ent)-0.1,max(data_BLP_familiarity$ent)+0.1) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

### Familiarity - Category

```{r}
ggplot(data_BLP_familiarity, aes(x=category,y=fam_mean)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_boxplot(fill="darkgrey") +
  labs(x = "Category", y = 'Familiarity accuracy') +
  scale_x_discrete(labels=c('Monolingual', 'Bilingual','Trilingual','Quadrilingual')) +
  ylim(min(data_BLP_familiarity$fam_mean)-0.05,max(data_BLP_familiarity$fam_mean)+0.05) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

```{r}
t.test(BLP_fam$fam_mean[BLP_fam$category=='mono'],mu=0.5);
t.test(BLP_fam$fam_mean[BLP_fam$category=='bi'],mu=0.5);
t.test(BLP_fam$fam_mean[BLP_fam$category=='tri'],mu=0.5);
t.test(BLP_fam$fam_mean[BLP_fam$category=='quadri'],mu=0.5);
```

# Clustering Tree

```{r}
data_BLP_short <- subset(data_BLP, select=c(HistoryL1Score,HistoryL2Score,HistoryL3Score,HistoryL4Score,
                                            UseL1Score,UseL2Score,UseL3Score,UseL4Score,
                                            ProficiencyL1Score,ProficiencyL2Score,ProficiencyL3Score,ProficiencyL4Score,
                                            AttitudeL1Score,AttitudeL2Score,AttitudeL3Score,AttitudeL4Score,
                                            L1Score,L2Score,L3Score,L4Score,
                                            var,ent,use_ent,cossim,use_cossim,multiexp,L1_L2_diff,
                                            RC3_L3,RC1_L4,RC2_use_L1vsL2,RC7_hist_L2,RC9_use_L4));
plot(varclus(as.matrix(data_BLP_short)))
```
