---
title: "BASL_v1_Ranalysis"
format: html
editor: visual
theme: superhero
page-layout: full
error: true
---

# SETUP

```{r}
# clear workspace
rm(list=ls());
ls();
```

```{r}
#| echo: true
#| output: false
# load required libraries
library(lme4);
library(Hmisc);
library(stats);
library(toolbox);
library(emmeans);
library(effects);
library(BayesRS);
library(extrafont);
library(showtext);
library(ggplot2);
library(viridis);
library(tidyverse);
library(DescTools);
library(paletteer);
library(BayesFactor);
library(RColorBrewer);
library(xtable);
library(corrplot);
library(psych);
library(sjPlot);
library(ggrepel);
library(png);
library(grid);
```

```{r}
# set global font
par(family="CMU Serif");
font_add("CMU Serif", "C:/Users/annal/Downloads/cmu/cmunrm.ttf");
showtext_auto();
```

```{r}
# set colour scheme
cols <- paletteer_d("MetBrewer::Degas");
cols2 <- paletteer_d("palettesForR::Named");
```

## Define Functions

### D Prime

```{r}
dPrime <- function(sbj, expectedResp, observedResp)
{
  sbjNumbers <- unique(sbj);
  dprimes <- vector(length=length(sbjNumbers), mode="numeric");
  log_beta <- vector(length=length(sbjNumbers), mode="numeric");
  c <- vector(length=length(sbjNumbers), mode="numeric");
  subjects <- vector(length=length(sbjNumbers), mode="integer");
  counter <- 1;
  for (s in sbjNumbers)
  {
    expectedRespCurrentSbj <- expectedResp[sbj==s];
    observedRespCurrentSbj <- observedResp[sbj==s];
    num_of_hits <- sum(observedRespCurrentSbj[expectedRespCurrentSbj==1])+.5;
    num_of_fa <- sum(observedRespCurrentSbj[expectedRespCurrentSbj==0])+.5;
    prop_of_hits <- num_of_hits/ (xtabs(~expectedRespCurrentSbj)[2]+1);
    prop_of_fa <- num_of_fa/ (xtabs(~expectedRespCurrentSbj)[1]+1);
    z_hits <- qnorm(prop_of_hits);
    z_fa <- qnorm(prop_of_fa); 
    dprimes[counter] <- round(z_hits - z_fa, digits = 3);
    log_beta[counter] <- round((z_fa^2 - z_hits^2)/2, digits = 3); #this is taken from Stanislaw and Todorov, PBR 1999. Log_beta=0 indicates no bias; negative values is bias for YES; positive values is bias for NO
    c[counter] <- round( -(z_hits + z_fa)/2, digits = 3); # this is taken again from Stanislaw and Todorov, PBR 1999, who note that c "...assumes that subjects respond yes when the decision variable exceeds the criterion and no otherwise; responses are based directly on the decision variable, which some researchers regard as more plausible than assuming that responses are based on a likelihood ratio [which the assumption behind beta] (Richardson, 1994). Another advantage of c is that it is unaffected by changes in d', whereas Beta is (Ingham, 1970; Macmil- lan, 1993; McNicol, 1972, pp. 63--64)". Similarly to log_beta, c=0 is no bias, negative c is bias for YES, negative c is bias for NO.
    subjects[counter] <- s;
    counter <- counter + 1;
  };
  data.frame(sbj=subjects, dprime=dprimes, log_beta=log_beta, c=c);
};
```

### Rounding

```{r}
round2 <- function(x, digits) {
  posneg = sign(x)
  z = abs(x)*10^digits
  z = z + 0.5 + sqrt(.Machine$double.eps)
  z = trunc(z)
  z = z/10^digits
  z*posneg
};
```

### LMER Export to LaTeX

```{r}
export_output <- function(model,name,pred_levels,
                         pred_type=c("categorical","continuous"),outcome_levels,
                         interaction=TRUE) {
  if (is.null(pred_type) || !length(pred_type) || !all(pred_type %in% c("categorical","continuous"))) {
    stop("'Predictor type' argument must be one of: 'categorical','continuous'")
  }
  
  # VARIABLES
  # trialn?
  vars <- all.vars(formula(model));
  if (vars[2] == "trialn") {
    trialn=TRUE;
  }  else {trialn=FALSE};
  
  # random effects?
  rand_vars <- toString(lme4::findbars(formula(model))[[1]])
  if (grepl("\\+",rand_vars)) {
    random_effects=TRUE
  } else {random_effects=FALSE};
  
  # interaction?
  formula_str <- toString(formula(model));
  if (grepl("\\*",formula_str)) {
    interaction=TRUE
  } else {interaction=FALSE};
  
  # FORMULA
  formula <- formula(summary(model));
  formula <- as.character(formula);
  formula <- paste(formula[2], formula[1], formula[3]);
  formula <- gsub("~", "$\\\\sim$", formula);
  formula <- gsub(" ","",formula);
  formula <- gsub("\\|", "\\\\textbar ", formula);
  formula <- gsub("expected", "string nature", formula);
  formula <- gsub("observed", "participant response", formula);
  name2 <- paste("\\multicolumn{5}{c}{\\textbf{",name,"}}",sep="");
  formula <- paste("\\multicolumn{5}{C{15cm}}{",formula,"}",sep="");
  formula <- data.frame(Groups=c(name2,formula),
                        Name=c("",""),
                        Variance=c("",""),
                        SD=c("",""),
                        Corr=c("",""));
  colnames(formula) <- c('\\textbf{Groups}','\\textbf{Name}',
                         '\\textbf{Variance}','\\textbf{SD}','\\textbf{Corr}');
  
  outcome_levels <- outcome_levels[-1];
  if (pred_type == "categorical") {
    pred_levels <- pred_levels[-1];
  }
  
  varcorr <- data.frame();
  if (random_effects) {
    # RANDOM EFFECTS
    varcorr <- data.frame(VarCorr(model));
    colnames(varcorr) <- c('Groups','Name','Var2','Variance','SD');
    if (length(outcome_levels) == 1) {
      varcorr$Corr <- c(0,varcorr$SD[nrow(varcorr)],0);
      colnames(varcorr) <- c('Groups','Name','Var2',
                             'Variance','SD','Corr');
      varcorr <- varcorr[-nrow(varcorr), ]
      varcorr <- varcorr[, -which(names(varcorr) == 'Var2')];
      varcorr[c('Variance','SD','Corr')] <- lapply(
        varcorr[c('Variance','SD','Corr')],
        function(x) round2(x,2));
      varcorr$Corr[varcorr$Corr == 0] <- "";
      varcorr$Groups[varcorr$Groups=='sbj_ID'] <- "";
      for (x in 1:length(outcome_levels)) {
        varcorr$Name[1+x] <- outcome_levels[x]
      };
      colnames(varcorr) <- c('\\textbf{Groups}','\\textbf{Name}',
                             '\\textbf{Variance}','\\textbf{SD}',
                             '\\textbf{Corr}');
      columns <- c('\\textbf{Random effects}','',
                   '\\textbf{Variance}','\\textbf{SD}','\\textbf{Corr}');
    }
    
    if (length(outcome_levels) == 2) {
      varcorr$Corr <- c(0,varcorr$SD[4],varcorr$SD[5]);
      varcorr$Corr2 <- c(0,0,varcorr$SD[6]);
      varcorr <- varcorr[-c((nrow(varcorr)-2):nrow(varcorr)), ]
      varcorr <- varcorr[, -which(names(varcorr) == 'Var2')];
      varcorr[c('Variance','SD','Corr','Corr2')] <- lapply(
        varcorr[c('Variance','SD','Corr','Corr2')],
        function(x) round2(x,2));
      varcorr$Corr[varcorr$Corr == 0] <- "";
      varcorr$Corr2[varcorr$Corr2 == 0] <- "";
      varcorr <- varcorr[, -which(names(varcorr) == 'Groups')];
      for (x in 1:length(outcome_levels)) {
        varcorr$Name[1+x] <- outcome_levels[x]
      };
      colnames(varcorr) <- c('\\textbf{Groups}','\\textbf{Name}',
                             '\\textbf{Variance}','\\textbf{SD}',
                             '\\textbf{Corr}');
      columns <- c('\\textbf{Random effects}','\\textbf{Variance}',
                   '\\textbf{SD}','\\textbf{Corr}','');
    };
    
    varcorr <- rbind(columns,varcorr)
    
    formula <- rbind(formula, varcorr);
  }
  
  # FIXED EFFECTS
  coefficients <- summary(model)$coefficients;
  coefs <- data.frame(coefficients);
  colnames(coefs) <- c('estimate','SE','z-value','p-value');
  
  coefs$sig <- "";
  coefs$sig[coefs$`p-value` < 0.1] <- " (.)";
  coefs$sig[coefs$`p-value` < 0.05] <- " (*)";
  coefs$sig[coefs$`p-value` < 0.01] <- " (**)";
  coefs$sig[coefs$`p-value` < 0.001] <- " (***)";
  
  coefs['p-value'] <- lapply(
    coefs['p-value'], 
    function(x) ifelse(
      abs(x)<=0.01,
      format(x,scientific=TRUE, digits=2),
      ifelse (x>0.04 & x<0.06, round2(x,3), round2(x,2))
    ));
  
  coefs[c('estimate','SE','z-value')] <- lapply(
    coefs[c('estimate','SE','z-value')], 
    function(x) ifelse(
      abs(x)<=0.01,
      format(x,scientific =TRUE, digits=2),
      round2(x,2)
    ));
  
  coefs$`p-value` <- paste(coefs$`p-value`,coefs$sig);
  coefs <- coefs[, -which(names(coefs) == 'sig')];
  
  columns <- c('\\textbf{Fixed effects}','$\\boldsymbol\\beta$','\\textbf{SE}',
               '\\textbf{z-value}','\\textbf{p-value}');
  rows <- c('(Intercept)');
  if (trialn) {
    rows <- c(rows,'scale(trialn)')
  };
  if (interaction == TRUE) {
    rows <- c(rows,outcome_levels);
  }
  for (level in pred_levels) {
    rows <- c(rows,level)
  }
  if (interaction == TRUE) {
    for (pred_level in pred_levels) {
      for (outcome_level in outcome_levels) {
        interaction <- paste(outcome_level,'*',pred_level,sep="")
        rows <- c(rows,interaction)
      }
    }
  }
  
  coefs <- cbind(rows,coefs);
  coefs <- rbind(columns,coefs);
  rownames(coefs) <- NULL;
  colnames(coefs) <- c('\\textbf{Groups}','\\textbf{Name}',
                       '\\textbf{Variance}','\\textbf{SD}','\\textbf{Corr}');
  
  global <- rbind(formula,coefs);
  
  filename <- paste('./analysis_tables/',name,".tex",sep="");
  
  if (random_effects) {
    hlines <- c(0,2,3,2+nrow(varcorr),3+nrow(varcorr),nrow(global));
  } else {
    hlines <- c(0,2,3,nrow(global));
  };
  
  print(xtable(global,auto=TRUE,booktabs=TRUE),
        file=filename,math.style.exponents=TRUE,latex.environments='center',
        include.rownames=FALSE,include.colnames=FALSE,
        tabular.environmen='tabularx',width="\\linewidth",
        hline.after=hlines,floating=FALSE,
        sanitize.text.function = function(x) {x});
  
  lines <- readLines(filename);
  lines <- gsub("\\\\begin\\{tabularx\\}\\{\\\\linewidth\\}\\{lllll\\}",
                "\\\\begin{tabularx}{\\\\linewidth}{{@{} >{\\\\RaggedRight}X*{5}{c}@{}}}",
                lines);
  lines <- gsub(" &  &  &  & ","",lines);
  lines <- gsub("\\\\hline","\\\\midrule",lines)
  writeLines(lines,filename);
};
```

## Set Directories

```{r}
# set working directory
setwd("C:/Users/annal/Documents/GitHub/affixproject");

# set analysis image output folder
output_folder <- "C:/Users/annal/Documents/Me/SISSA/BASL/BASL analysis/exp1";
```

## Input Participant IDs

```{r}
participants <- list("5aa787c66219a30001c765f8","5ae5db897edeb000014a85ee","5b212164cfbf200001cfb3ad","5b213220809d160001a2c36d","5bcd11401662020001fe82c1","5c19254b0b9f6b00014769ee","5c1bfabab0fcc900019d9ff4","5caccaed2f93d700157b4782","5cbe02ab39447e0001745a5e","5cefe8856e0eec00015971dd","5d9a125f1714540016a40a27","5dab6e7d80e1780016d5bc9b","5dcb33ab0550ef819f508abf","5e12048c7605fe8839180a14","5e283f8ad48ecf000ddd0724","5e2c6968e97bec29709a53c6","5e3ff59bf2160b23942ada93","5e42b6421f44d3143440b25c","5e42f03607b468000d8eb912","5e433ed3393e971e19f4735d","5e577e79ce30ae13226e61ae","5e6d3324f14d262fced5bbfe","5e87b28549538b0fdf96b318","5e89e89bf025be000c01eead","5e8b66490d48450346bf2755","5e8c57d9b4483e012006e7aa","5e8e55509422bb10abed1f54","5e9bd025eb6b380e1d66d04c","5ea171c1a8782801263e7540","5ea9611edec14d052ada0bae","5ea9cd383b32cf15448a86ac","5eaae42f19a24d05cbd6ccb4","5eaf1c50f3540c614eb973a5","5eb35dff41a381156be161c2","5eb71c59c55b3b0ce571ae7c","5ebc0c153f8b2e04d3833423","5ec12ed7a66dbf01c7d740c1","5ec1c01a8ccaaa5ec0080c91","5ec6d06c67b0da0fb6f85e83","5ecbb4c00bc62403dae2df59","5ecd21dec04cca02c9032485","5ed013f88fce6e0d858b732e","5ee623674afa60375e30eec3","5ee83da8817af0000d47448f","5ee942381a22491bbb7170f8","5eef3de3fb4e031bf546d887","5efd2964d36f63162f263795","5f0471a92ec97b6d1aec7739","5f09d989eff16b266fba44c0","5f0d65ef2ad0c60009209f0f","5f0f93938935de000855898b","5f11c9f84078cd0888177499","5f18a80367ef6b0bbc5f3720","5f19fa0f3e85b20d0336258c","5f1e8dc7e2161c86cdcd220a","5f219602670e5a0af2cf5237","5f33289c1fe9181376ee67d9","5f33c58329beab1f63c0dfaa","5f350f459bf003464a03ea5e","5f47e34858dd331165bf9f00","5f5a713d37f71112463ab4d9","5f5e7de4c81d3672642cd612","5f6cd5ce1758e90f12ae1123","5f708f5f0d32bb66960d4473","5f784f5b98f4963cdf902340","5f7bd801486f5e1ce581980f","5f858743256d25036d9fa693","5f91dc284909fe0b08f9e2e1","5f99cee5a2a7d109a1624e10","5fa4258658811d03fbc6ce8b","5fa4725a186c050edc3bcc20","5fa5793490f10705755818c0","5fa59d4d5a29c90da975efe9","5fc2d2d79da439201ab6addc","5fc44d83862e3e79b02e0438","5fc781689771f106330abf6a","5fd2416e5061f30735e202e9","5fd69a0014c3b25ee539f66b","5fd9c5c67fa7c74ec42bb318","5fdbf74c5474cd11e39eeaf3","5fe2308a91773957e88b89be","600e0dadada7da69afc5b3de","600f0f9c3bfcdc077c924e51","60123adc24c9f126819861b6","601705a0246e51313e8ed38e","601951245f481e000980504f","601b5c79e845ac360826c9df","601ffb441dc6d959b855eea5","602bb123612bfe330818d4ef","6042a56575ab0c1ccffc3152","60491025dd8eb31e48a0ca8d","60536ffae4f98513b671f482","605aa0bb5fb71bbcf0808892","60645fe61129208791535d15","6065d7d47409810344f7e6bb","60664619eac28843177fee96","60670ac0fc7e169231369ab1","606dc21c1ce7dc64af9d81fb","6074768dc48e0753011d3d72","607ea5504e74d104da5a108a","60883a7e91c0be66dbb96fc8","608858869a591bd129fbbc6c","608c2e566d92c2aa3543e2d2","608c64e14968cdd8dcbe1be4","6092e2aac56871319199b6a5","6093cacf9a39751eedd55916","60957b300f08087b0af0031c","60a3fe2d888e7a090d6d8f82","60a68725b2b424dc0d7ce793","60b7b8126c0c4524e913236e","60bbe0da43325dadf2b1b6a9","60c49e68081928c86ba7b98a","60d478e72e8251287b641b2d","60d7605d7af8d66774061717","60db4aed5dd7b87124f51341","60dee3200c7c3355c62326d9","60e12640be1b69b66053d55b","60e3b18d3d4205b4c52ada56","60e9ea97d19e613e60a994da","60eb26fb8db6845a14fe5a91","60ec51c51a3158a50ded8a3e","60edd136d544e7c8f5fac8a7","60f030dca19a06db1b50d16a","60f56f0103876eae7c0d870f","60f579085ebf24f9c80f223e","60f6b8f8e574e14634ead43e","60f88d7fef1959734061e5a7","60fd0f49858465796afd5da9","6100174f92a7a0e5141b195e","61001b6892ebd05a24fe82e1","61055020201a7da5a704f7dd","6107d788163252e3b5c348e3","610834993bac40f050062896","610958b8473c7b96e4bd207d","610a52647a452dee7ca89360","610d2275ba5f1ee0fdcee3e8","610f2eabb45be8717fc155e0","61125e23136464bd2cbbefc9","61143bd22a1649da3b52ae32","611bdb0fed7c9df6dce28c3f","611cebb780fbae98c5bcc84d","611dc53f0098557586e89b17","611e7d1295185bf6f56fd951","611e9c16e90a0d4c6f0d8df5","611eafa6011b0423f7d7230f",
                     "611eeafa283a2d1f57537fea","6120211d8e1eab16fcb7ad69","6122966a93af160af481836c","6124a4ba3df07e768bd9c90b","61275a3158c67415afb971ff","612a98181f4b6d1cf01f926c","61301fcb49db2f170cb02b93","6131f7010e926c9103558040","613867f34e206e4f573bc6ef","613a73d06cf1fcfef304d3fa","613ab1e64acd61ebd0a7116d","613f57084e80f056c78f9b7b","6140f1c4ead758f1b72bbe2f","6140ff9c5750f0081ca8d71f","6144742e57a61e489cc9e978","6147aed5b2a4f748dc2b6ba4","614b323022fcd8b7408005a6","614c80483d06dcf7ad552679","614c8e5469405530dc27b9d5","614dd6473c74b217ad73cc9c","61520b079436973e05f72d33","61548fa2b637194e04c9bc09","6155e204cc071b306458dfff","6156a440279fdf408ee663ae","6156b68cc77b48d6693b361c","615b042301e3a24311563ee4","615b1ab789b14c9996251fb4","615b41767003d4ece749ed9d","615da9ee365ab7d547b98979","615f371e6688c87e53e7acf5","61616ce2bb94584e11c911af","6163faf9d9ac4586fe776568","616494f1ae4537c01914c758","616631efeeac0979c1ba85a9","616891e25a026e1f7262116c","616eb493bb7e4ab4fa1de8d4","6170821d1e8ffb9c893b28a4","6171349b89a54d4823f9eca1","617142c2a843eef6f8f148b6","6171d922c871ba795b6a4827","6172078b966225960be2a7b5","617679054948369cb824d837","63ee5d8aaee278de46b7d4cc","6455490f7c5f35e4221a810a","64764d56699f097a96ec6e5c","64973d83e4fc64d6ae59c370","64a288758b7c82ff2d18da75","64ef422a4789bd6b6b9042ce","65032a60861e9a17bc1a7444","65089e7ce53888b0b3840c62","650aee87054446f772acdfcc");
```

# TESTING

```{r}
# importing testing data
data_all_testing <- read.csv("testing_preprocessed_clean.csv",header=T,sep=",");
data_all_testing <- subset(data_all_testing, select = -c(X)) # remove redundant column added by Pavlovia
data_testing <- data_all_testing[data_all_testing$sbj_ID %in% participants,]; # n = 196 participants

# make some variables factors
data_testing$sbj_ID <- as.factor(data_testing$sbj_ID);
data_testing$task <- as.factor(data_testing$task);
data_testing$item <- as.factor(data_testing$item);
data_testing$testing_condition <- as.factor(data_testing$testing_condition);
data_testing$correct <- as.logical(data_testing$correct);

# change coding: 0 into 'within_lang' and 1 into 'between_lang'
data_expected <- replace(data_testing$expected, data_testing$expected == 0, 'within_lang');
data_expected <- replace(data_expected, data_expected == 1, 'between_lang');
data_testing$expected <- data_expected;
data_testing$expected <- as.factor(data_testing$expected);

data_observed <- replace(data_testing$observed, data_testing$observed == 0, 'within_lang');
data_observed <- replace(data_observed, data_observed == 1, 'between_lang');
data_testing$observed <- data_observed;
data_testing$observed <- as.factor(data_testing$observed);

# exclude 1 participant said "yes" to all BLP use questions
data_testing <- data_testing[!data_testing$sbj_ID %in% c('615b41767003d4ece749ed9d'),];
# now n=195
```

## Testing RTs

```{r}
IDs <- list(data_testing$sbj_ID);
IDs <- sapply(IDs, unique);
plot(density(data_testing$rt[data_testing$sbj_ID==IDs[1]],na.rm=TRUE),xlim=c(0,2200),ylim=c(0,0.01),xlab="RTs (ms)",main="",xaxt = "n",col=cols2[27],yaxs="i",lwd=1,cex.lab=1.5);
axis(1, at = c(0,200,400,600,800,1000,1200,1400,1600,1800,2000,2200));
for (x in 2:195) {
  lines(density(data_testing$rt[data_testing$sbj_ID==IDs[x]],na.rm=TRUE),col=cols2[x+26],lwd=1)
}; # good, centered around 800ms
data_testing_rt_means <- aggregate(data_testing$rt, list(data_testing$sbj_ID), FUN=mean, na.rm=TRUE);
summary(data_testing_rt_means$x); # good med & mean
plot(data_testing_rt_means$x, ylab="Mean participant RT (ms)",xlab="Participants",main="",xaxt = "n",pch=3,yaxs="i",ylim=c(0,2750))
# looks healthy overall

## problematic participant RTs ##
summary(data_testing$rt[data_testing$sbj_ID=="5e8b66490d48450346bf2755"]);
plot(data_testing$rt[data_testing$sbj_ID=="5e8b66490d48450346bf2755"],ylim=c(2000,170000),pch=19);
# exclude 5e8b66490d48450346bf2755: mean RT of 2627 slow, lots of slow trials, max of 162188 VERY slow
data_testing <- data_testing[!data_testing$sbj_ID %in% c('5e8b66490d48450346bf2755'),];
data_testing_rt_means <- data_testing_rt_means[!data_testing_rt_means$Group.1 %in% c('5e8b66490d48450346bf2755'),]
# now n=194

summary(data_testing$rt[data_testing$sbj_ID=="615b042301e3a24311563ee4"]);
plot(data_testing$rt[data_testing$sbj_ID=="615b042301e3a24311563ee4"],ylim=c(2000,170000),pch=19);
# exclude 615b042301e3a24311563ee4: mean RT of 2080 slow, lots of slow trials, max of 62155 very slow
data_testing <- data_testing[!data_testing$sbj_ID %in% c('615b042301e3a24311563ee4'),];
data_testing_rt_means <- data_testing_rt_means[!data_testing_rt_means$Group.1 %in% c('615b042301e3a24311563ee4'),]
# now n=193
summary(data_testing_rt_means$x);
```

## Testing Responses

```{r}
# due to technical issue: n(0M)=40, n(1M)=37, n(2M)=34
total_0M <- 40;
total_1M <- 37;
total_2M <- 34;

# yes responses globally
mean_yes <- aggregate(data_testing$observed,by=list(data_testing$sbj_ID), FUN=function(x) sum(x == 'within_lang'));
names(mean_yes) <- c("sbj_ID", "yes");
summary(mean_yes$yes);
# no one responding only "yes" or never "yes"
```

### 0M Responses

```{r}
data_testing_0M_yes <- aggregate(data_testing$observed[data_testing$testing_condition=='0M'], by=list(data_testing$sbj_ID[data_testing$testing_condition=='0M']), FUN = function(x) sum(x == 'within_lang'));
names(data_testing_0M_yes) <- c("sbj_ID","yes_0M");
data_testing_0M_yes$yes_0M <- data_testing_0M_yes$yes_0M/total_0M*100; #transform into percent
summary(data_testing_0M_yes$yes_0M);
t.test(data_testing_0M_yes$yes_0M, mu=50);
# 0M "yes" not sig above chance
data_testing <- merge(data_testing,data_testing_0M_yes,by="sbj_ID");
```

### 1M Responses

```{r}
data_testing_1M_yes <- aggregate(data_testing$observed[data_testing$testing_condition=='1M'], by=list(data_testing$sbj_ID[data_testing$testing_condition=='1M']), FUN = function(x) sum(x == 'within_lang'));
names(data_testing_1M_yes) <- c("sbj_ID","yes_1M");
data_testing_1M_yes$yes_1M <- data_testing_1M_yes$yes_1M/total_1M*100; #transform into percent
summary(data_testing_1M_yes$yes_1M);
t.test(data_testing_1M_yes$yes_1M, mu=50);
# sig above chance
data_testing <- merge(data_testing,data_testing_1M_yes,by="sbj_ID");
```

### 2M Responses

```{r}
data_testing_2M_yes <- aggregate(data_testing$observed[data_testing$testing_condition=='2M'], by=list(data_testing$sbj_ID[data_testing$testing_condition=='2M']), FUN = function(x) sum(x == 'within_lang'));
names(data_testing_2M_yes) <- c("sbj_ID","yes_2M");
data_testing_2M_yes$yes_2M <- data_testing_2M_yes$yes_2M/total_2M*100; #transform into percent
summary(data_testing_2M_yes$yes_2M);
t.test(data_testing_2M_yes$yes_2M, mu=50);
# sig above chance
data_testing <- merge(data_testing,data_testing_2M_yes,by="sbj_ID");

data_testing_2M_aggr <- data_testing %>% 
  mutate(correct01 = case_when(correct == TRUE ~ 1,
                               correct == FALSE ~ 0),
         yesno01 = case_when(observed == 'between_lang' ~ 0,
                             observed == 'within_lang' ~ 1)) %>% 
  filter(testing_condition == '2M') %>% 
  group_by(expected, sbj_ID) %>% 
  dplyr::summarise(meanCorrect = mean(correct01), se = sd(correct01/sqrt(n())),
                   meanYes = mean(yesno01), se = sd(yesno01/sqrt(n()))) %>% 
  mutate(meanNo = 1 - meanYes);

data_testing_2M_aggr <- data_testing_2M_aggr %>%
  pivot_longer(
    cols = c(meanYes, meanNo),
    names_to = "response",
    values_to = "meanValue"
  );

data_testing_2M_aggr$response <- as.factor(data_testing_2M_aggr$response);

ggplot(data_testing_2M_aggr[ which(data_testing_2M_aggr$response=='meanYes'),], aes(x=expected, y=meanValue, fill=expected)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  geom_boxplot(width=0.1,position=position_dodge(width=1)) +
  scale_fill_manual(values=c(cols2[100],cols2[200]),
                    name="Participant response",labels=c("Between-language","Within-language")) +
  scale_x_discrete(labels=c('Between-language', 'Within-language')) +
  labs(x = "String nature", y = 'Proportion of "within-language" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="none",
        legend.background=element_rect(fill=NA));
```

### 2M Scores

```{r}
data_testing_2M_means <- aggregate(data_testing$correct[data_testing$testing_condition=='2M'], list(data_testing$sbj_ID[data_testing$testing_condition=='2M']), FUN=mean, na.rm=TRUE);
names(data_testing_2M_means) <- c("sbj_ID","score_2M");

ggplot(data_testing_2M_means, aes(x="", y=score_2M)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_boxplot(fill="grey") +
  ylim(0,1) +
  labs(y='Participant 2M scores') +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));

summary(data_testing_2M_means$score_2M);
var(data_testing_2M_means$score_2M);
plot(data_testing_2M_means$score_2M,pch=3,ylim=c(0,1));
abline(h=0.5, lty=5); # clustered around chance
hist(data_testing_2M_means$score_2M); # normally distributed
t.test(data_testing_2M_means$score_2M, mu=0.50);
# not sig different from chance
data_testing <- merge(data_testing,data_testing_2M_means,by="sbj_ID");
```

### d' Computations

```{r}
data_testing_2M <- data_testing[data_testing$testing_condition == '2M',];

data_testing_2M$expected_bi[data_testing_2M$expected == "between_lang"] <- 0;
data_testing_2M$expected_bi[data_testing_2M$expected == "within_lang"] <- 1;
data_testing_2M$observed_bi[data_testing_2M$observed == "between_lang"] <- 0;
data_testing_2M$observed_bi[data_testing_2M$observed == "within_lang"] <- 1;

dprimes2M <- dPrime(data_testing_2M$sbj_ID, data_testing_2M$expected_bi, data_testing_2M$observed_bi);
names(dprimes2M) <- c("sbj_ID","dprime","log_beta","c");
summary(dprimes2M);
# mean(d') = -0.02, mean(c) = -0.37
data_testing <- merge(data_testing,dprimes2M,by="sbj_ID");
cor.test(data_testing$dprime,data_testing$c, method="pearson"); 
# significant positive moderate correlation
# more "YES" responses helps you respond more accurately

testing_short <- data_testing[!duplicated(data_testing$sbj_ID), ];
t.test(testing_short$dprime, mu=0);
# not sig different from chance
t.test(testing_short$c, mu=0);
# sig above chance
```

### "Yes" Responses across Conditions

```{r}
# evaluating the differences between conditions
data_testing_conditions <- merge(data_testing_0M_yes,data_testing_1M_yes, by='sbj_ID');
data_testing_conditions <- merge(data_testing_conditions,data_testing_2M_yes, by='sbj_ID');
conditions_table <- table(data_testing$testing_condition, data_testing$observed);
chisq.test(conditions_table);
data_testing_conditions <- data_testing_conditions %>%
  gather(condition, score, -sbj_ID);
data_testing_conditions$score <- data_testing_conditions$score/100;

# plotting all "yes" responses across conditions
ggplot(data_testing_conditions, aes(x = condition, y = score, color = condition)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_jitter(width = 0.1, height = 0, alpha = 0.3,color= "black",size=2) +
  labs(x = "Condition", y = 'Proportion of "yes" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20)) +
  ylim(0,1.01) +
  stat_summary(geom = "point",fun = "mean",col = "red",size = 4,shape = 19) +
  stat_summary(geom = "errorbar", fun.data = "mean_se", width = 0.1,col="red",position = position_dodge(width = 0.5)) +
  scale_x_discrete(labels=c("0M", "1M", "2M"));

# 2M accuracy*RTs
cor.test(data_testing_2M_means$score_2M, data_testing_rt_means$x, method="pearson");
# non-significant correlation
```

## Strategies

```{r}
strats <- subset(data_testing, select = c(sbj_ID, strategy));
strats <- strats[!duplicated(strats),];
write.csv(strats,"BASL_exp1_strats.csv", row.names = FALSE);
```

### Chunks

```{r}
chunkID_strategists <- list('5caccaed2f93d700157b4782','5e577e79ce30ae13226e61ae','5e8c57d9b4483e012006e7aa','5eaae42f19a24d05cbd6ccb4','5ecbb4c00bc62403dae2df59','5ee942381a22491bbb7170f8','5f18a80367ef6b0bbc5f3720','5f5a713d37f71112463ab4d9','5fc2d2d79da439201ab6addc','600f0f9c3bfcdc077c924e51','60123adc24c9f126819861b6','601705a0246e51313e8ed38e','601ffb441dc6d959b855eea5','60491025dd8eb31e48a0ca8d','60664619eac28843177fee96','60db4aed5dd7b87124f51341','60f6b8f8e574e14634ead43e','60fd0f49858465796afd5da9','6144742e57a61e489cc9e978','61520b079436973e05f72d33','615b1ab789b14c9996251fb4','615da9ee365ab7d547b98979','616891e25a026e1f7262116c','63ee5d8aaee278de46b7d4cc','6455490f7c5f35e4221a810a');
data_chunkIDstrategists <- data_testing[data_testing$sbj_ID %in% chunkID_strategists,];
data_chunkIDstrategists <- data_chunkIDstrategists[data_chunkIDstrategists$testing_condition=='2M',];
data_chunkIDstrategists <- data_chunkIDstrategists[!duplicated(data_chunkIDstrategists$sbj_ID), ];
data_chunkIDstrategists$strat <- "chunkID";
summary(data_chunkIDstrategists$score_2M);
t.test(data_chunkIDstrategists$score_2M, mu=0.50);
# not sig different from chance
summary(data_chunkIDstrategists$dprime);
summary(data_chunkIDstrategists$c);
# dprime:0.10 c:-0.34

ggplot(data_chunkIDstrategists, aes(x="", y=score_2M)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,fill="gold1") +
  geom_boxplot(width=0.1,fill="gold1") +
  ylim(0,1) +
  labs(y='Participant 2M scores') +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### Intuition

```{r}
intuition_strategists <- list('5aa787c66219a30001c765f8','5ae5db897edeb000014a85ee','5b213220809d160001a2c36d','5bcd11401662020001fe82c1','5c1bfabab0fcc900019d9ff4','5dab6e7d80e1780016d5bc9b','5dcb33ab0550ef819f508abf','5e12048c7605fe8839180a14','5e3ff59bf2160b23942ada93','5e89e89bf025be000c01eead','5e8e55509422bb10abed1f54','5e9bd025eb6b380e1d66d04c','5ea9611edec14d052ada0bae','5ea9cd383b32cf15448a86ac','5eaf1c50f3540c614eb973a5','5eb35dff41a381156be161c2','5ec6d06c67b0da0fb6f85e83','5ecd21dec04cca02c9032485','5ed013f88fce6e0d858b732e','5ee623674afa60375e30eec3','5ee83da8817af0000d47448f','5f0471a92ec97b6d1aec7739','5f0d65ef2ad0c60009209f0f','5f11c9f84078cd0888177499','5f18a80367ef6b0bbc5f3720','5f19fa0f3e85b20d0336258c','5f1e8dc7e2161c86cdcd220a','5f219602670e5a0af2cf5237','5f47e34858dd331165bf9f00','5f5e7de4c81d3672642cd612','5f708f5f0d32bb66960d4473','5f858743256d25036d9fa693','5f91dc284909fe0b08f9e2e1','5fa5793490f10705755818c0','5fa59d4d5a29c90da975efe9','5fc44d83862e3e79b02e0438','5fc781689771f106330abf6a','5fd2416e5061f30735e202e9','5fd9c5c67fa7c74ec42bb318','5fe2308a91773957e88b89be','600e0dadada7da69afc5b3de','6042a56575ab0c1ccffc3152','605aa0bb5fb71bbcf0808892','60645fe61129208791535d15','606dc21c1ce7dc64af9d81fb','608858869a591bd129fbbc6c','60957b300f08087b0af0031c','60a3fe2d888e7a090d6d8f82','60a68725b2b424dc0d7ce793','60bbe0da43325dadf2b1b6a9','60d7605d7af8d66774061717','60dee3200c7c3355c62326d9','60ec51c51a3158a50ded8a3e','60f030dca19a06db1b50d16a','6100174f92a7a0e5141b195e','61001b6892ebd05a24fe82e1','610f2eabb45be8717fc155e0','61125e23136464bd2cbbefc9','611bdb0fed7c9df6dce28c3f','611cebb780fbae98c5bcc84d','611e9c16e90a0d4c6f0d8df5','611eeafa283a2d1f57537fea','6131f7010e926c9103558040','613867f34e206e4f573bc6ef','613a73d06cf1fcfef304d3fa','6140ff9c5750f0081ca8d71f','614c80483d06dcf7ad552679','614c8e5469405530dc27b9d5','614dd6473c74b217ad73cc9c','6155e204cc071b306458dfff','6156a440279fdf408ee663ae','6156b68cc77b48d6693b361c','61616ce2bb94584e11c911af','6170821d1e8ffb9c893b28a4','6171349b89a54d4823f9eca1','617142c2a843eef6f8f148b6','6171d922c871ba795b6a4827','6172078b966225960be2a7b5','65032a60861e9a17bc1a7444','65089e7ce53888b0b3840c62');
data_intuitionstrategists <- data_testing[data_testing$sbj_ID %in% intuition_strategists,];
data_intuitionstrategists <- data_intuitionstrategists[data_intuitionstrategists$testing_condition=='2M',];
data_intuitionstrategists <- data_intuitionstrategists[!duplicated(data_intuitionstrategists$sbj_ID), ];
data_intuitionstrategists$strat <- "intuition";
summary(data_intuitionstrategists$score_2M);
t.test(data_intuitionstrategists$score_2M, mu=0.50);
# not sig different from chance
summary(data_intuitionstrategists$dprime);
summary(data_intuitionstrategists$c);
# dprime:-0.04 c:-0.31

ggplot(data_intuitionstrategists, aes(x="", y=score_2M)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,fill="palevioletred") +
  geom_boxplot(width=0.1,fill="palevioletred") +
  ylim(0,1) +
  labs(y='Participant 2M scores') +
  theme(axis.title.x=element_blank(),axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### Comparison

```{r}
scores_strategies <- rbind(data_chunkIDstrategists,data_intuitionstrategists);
ggplot(scores_strategies, aes(x=strat, y=score_2M, fill=strat)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  geom_boxplot(width=0.1,position=position_dodge(width=1)) +
  ylim(0,1) +
  scale_fill_manual(values=c("gold1","palevioletred")) +
  scale_x_discrete(labels=c('Chunk ID', 'Intuition')) +
  labs(x="Strategy used",y="Participant 2M scores") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="none",legend.background=element_rect(fill=NA));
```

# FAMILIARITY

```{r}
data_all_familiarity <- read.csv("exp1_familiarity_preprocessed.csv",header=T,sep=",");
data_all_familiarity <- subset(data_all_familiarity, select = -c(X)) # remove redundant column added by Pavlovia
data_familiarity <- data_all_familiarity[data_all_familiarity$sbj_ID %in% participants,]; # n = 187 participants
data_familiarity <- data_familiarity[!data_familiarity$sbj_ID %in% c('615b042301e3a24311563ee4','5e8b66490d48450346bf2755','615b41767003d4ece749ed9d'),];

# make some variables factors
data_familiarity$sbj_ID <- as.factor(data_familiarity$sbj_ID);
data_familiarity$task <- as.factor(data_familiarity$task);
data_familiarity$correct <- as.logical(data_familiarity$correct);
data_familiarity$target <- as.factor(data_familiarity$target);
data_familiarity$confound <- as.factor(data_familiarity$confound);
```

## Familiarity Accuracy

```{r}
data_familiarity_means <- aggregate(data_familiarity$correct, list(data_familiarity$sbj_ID), FUN=mean);
colnames(data_familiarity_means)[colnames(data_familiarity_means)=="Group.1"]="sbj_ID";
colnames(data_familiarity_means)[colnames(data_familiarity_means)=="x"]="fam_mean";
summary(data_familiarity_means$fam_mean);
hist(data_familiarity_means$fam_mean); # mostly normally distributed
t.test(data_familiarity_means$fam_mean, mu=0.50);
# sig above chance
var(data_familiarity_means$fam_mean);
data_familiarity <- merge(data_familiarity,data_familiarity_means,by="sbj_ID");

# familiarity accuracy violin plot
ggplot(data_familiarity_means, aes(y=fam_mean, x=x)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_violin(alpha=0.75,fill="orchid4") +
  geom_boxplot(width=0.1,fill="orchid4") +
  ylim(0,1) +
  scale_fill_manual(values=cols2[350]) +
  labs(y = 'Proportion of correct familiarity responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),legend.position = "none",
        axis.title.x=element_blank(),axis.text.x=element_blank(),
        axis.ticks.x=element_blank());
```

## Familiarity RTs

```{r}
IDs <- list(data_familiarity$sbj_ID);
IDs <- sapply(IDs, unique);
plot(density(data_familiarity$rt[data_familiarity$sbj_ID==IDs[1]]),xlim=c(0,4000),ylim=c(0,0.01),xlab="Familiarity RTs (ms)",main="",xaxt = "n",col=cols2[1],lwd=2,yaxs="i");
axis(1, at = c(0,500,1000,1500,2000,2500,3000,3500,4000));
for (x in 2:193) {
  lines(density(data_familiarity$rt[data_familiarity$sbj_ID==IDs[x]]),col=cols2[x],lwd=2)
};
data_familiarity_rt_means <- aggregate(data_familiarity$rt, list(data_familiarity$sbj_ID), FUN=mean, na.rm=TRUE);
summary(data_familiarity_rt_means$x);

# familiarity accuracy*RTs
cor.test(data_familiarity_means$fam_mean, data_familiarity_rt_means$x, method="pearson")
# slower at responding = better accuracy
```

## Comparisons with Testing

```{r}
# familiarity accuracy*testing accuracy
cor.test(data_familiarity_means$fam_mean, data_testing_2M_means$score_2M, method="pearson");
# higher familiarity = better 2M scores

# familiarity accuracy by testing strategy
data_strategistsfam <- data_familiarity_means;
data_strategistsfam$strat[data_strategistsfam$sbj_ID %in% intuition_strategists] <- 'intuition';
data_strategistsfam$strat[data_strategistsfam$sbj_ID %in% chunkID_strategists] <- 'chunks';
data_strategistsfam$strat[data_strategistsfam$sbj_ID %in% chunkID_strategists] <- 'chunks';
data_strategistsfam$strat <- data_strategistsfam$strat %>% replace_na('other');

summary(data_strategistsfam$fam_mean[data_strategistsfam$strat=='chunks']);
t.test(data_strategistsfam$fam_mean[data_strategistsfam$strat=='chunks'],mu=0.50);
# significantly above chance

summary(data_strategistsfam$fam_mean[data_strategistsfam$strat=='intuition']);
t.test(data_strategistsfam$fam_mean[data_strategistsfam$strat=='intuition'],mu=0.50);
# significantly above chance

par(mar=c(5,5,2,2));
boxplot(data_strategistsfam$fam_mean~data_strategistsfam$strat,ylab = "Familiarity score",xlab="Testing strategy",ylim=c(0.28,0.9),cex.lab=2,cex.axis=1.75,yaxs="i");
abline(h=0.5, lty=5);
par(mar=c(5, 4, 4, 2) + 0.1); # back to default
```

# BLP

```{r}
data_all_BLP <- read.csv("exp1_BLP_preprocessed.csv",header=T,sep=",");
data_all_BLP <- subset(data_all_BLP, select = -c(X)); # remove redundant column added by Pavlovia
data_BLP <- data_all_BLP[data_all_BLP$sbj_ID %in% participants,]; # n = 190 participants
data_BLP <- subset(data_BLP, select = -c(AoAgioL1, AoAgioL2, AoAgioL3, AoAgioL4, anniInstrL1, anniInstrL2, anniInstrL3, anniInstrL4, anniPaeseL1, anniPaeseL2, anniPaeseL3, anniPaeseL4, anniFamigliaL1, anniFamigliaL2, anniFamigliaL3, anniFamigliaL4, anniLavoroL1, anniLavoroL2, anniLavoroL3, anniLavoroL4, PercAmiciL1, PercAmiciL2, PercAmiciL3, PercAmiciL4, PercFamigliaL1, PercFamigliaL2, PercFamigliaL3, PercFamigliaL4, PercLavoroL1, PercLavoroL2, PercLavoroL3, PercLavoroL4, PercStessoL1, PercStessoL2, PercStessoL3, PercStessoL4, PercCalcoliL1, PercCalcoliL2, PercCalcoliL3, PercCalcoliL4, ProfParlaL1, ProfParlaL2, ProfParlaL3, ProfParlaL4, ProfCapisceL1, ProfCapisceL2, ProfCapisceL3, ProfCapisceL4, ProfLeggeL1, ProfLeggeL2, ProfLeggeL3, ProfLeggeL4, ProfScriveL1, ProfScriveL2, ProfScriveL3, ProfScriveL4, AttMiStessoL1, AttMiStessoL2, AttMiStessoL3, AttMiStessoL4, AttCulturaL1, AttCulturaL2, AttCulturaL3, AttCulturaL4, AttLivNativoL1, AttLivNativoL2, AttLivNativoL3, AttLivNativoL4, AttMadrelinguaL1, AttMadrelinguaL2, AttMadrelinguaL3, AttMadrelinguaL4));
data_BLP <- data_BLP[!data_BLP$sbj_ID %in% c('615b042301e3a24311563ee4','5e8b66490d48450346bf2755','615b41767003d4ece749ed9d'),];

BLP_correction <- function(data_BLP)
{
  data_BLP[data_BLP == "polish"|data_BLP == "POLISH"] <- "Polish";
  data_BLP[data_BLP == "english"|data_BLP=="ENGLISH"|data_BLP=="Englsih"|data_BLP=="Englsh"|data_BLP=="British"|data_BLP=="Engllish"|data_BLP=="ENGLISH "|data_BLP=="English "|data_BLP=="ENGLISH"|data_BLP=="english"|data_BLP=="english "|data_BLP=="englis"|data_BLP=="eanglish"|data_BLP=="Enlish"] <- "English";
  data_BLP[data_BLP == "portuguese"|data_BLP == "portuguese"|data_BLP == "Portugal"|data_BLP=="Potuguese"] <- "Portuguese";
  data_BLP[data_BLP =="SPANISH"|data_BLP=="Spnsh"|data_BLP=="spanish"] <- "Spanish";
  data_BLP[data_BLP == "ITALIAN"|data_BLP=="italian"] <- "Italian";
  data_BLP[data_BLP == "sotho"] <- "Sotho";
  data_BLP[data_BLP == "greek"|data_BLP=="Greece"] <- "Greek";
  data_BLP[data_BLP == "tshivenda"] <- "Tshivenda";
  data_BLP[data_BLP == "Gujrau"] <- "Gujarati"; # to check
  data_BLP[data_BLP == "ukrainian"|data_BLP=="ukranian"] <- "Ukrainian";
  data_BLP[data_BLP == "SETSWANA"] <- "Setswana";
  data_BLP[data_BLP == "afrikaans"] <- "Afrikaans";
  data_BLP[data_BLP == "punjabi"] <- "Punjabi";
  data_BLP[data_BLP == "siswati"] <- "Siswati";
  data_BLP[data_BLP == "Germany"|data_BLP=="german"|data_BLP=="germany"|data_BLP=="GERMANY"|data_BLP=="GERMAN"|data_BLP=="Deustch"|data_BLP == "Deutch"] <- "German";
  data_BLP[data_BLP == "russian"] <- "Russian";
  data_BLP[data_BLP == "Isiulu"] <- "IsiZulu";
  data_BLP[data_BLP == "ZULU"|data_BLP=="zulu"] <- "Zulu";
  data_BLP[data_BLP == "northern sotho"] <- "Northern Sotho";
  data_BLP[data_BLP == "chinese"] <- "Chinese";
  data_BLP[data_BLP == "sesotho"|data_BLP=="SESOTHO"] <- "Sesotho";
  data_BLP[data_BLP == "sepedi"] <- "Sepedi";
  data_BLP[data_BLP == "TSHIVENDA"] <- "Tshivenda";
  data_BLP[data_BLP == "arabic"] <- "Arabic";
  data_BLP[data_BLP == "XHOSA"|data_BLP=="xhosa"] <- "Xhosa";
  data_BLP[data_BLP == "french"|data_BLP=="fRANCH"] <- "French";
  data_BLP[data_BLP == "hungarian"] <- "Hungarian";
  data_BLP[data_BLP == "POLISH"] <- "Polish";
  data_BLP[data_BLP == "croatian"] <- "Croatian";
  data_BLP[data_BLP == "bosnian"] <- "Bosnian";
  data_BLP[data_BLP == "madarin"] <- "Mandarin";
  data_BLP[data_BLP == "Icelandic and German"] <- "Icelandic";
  data_BLP[data_BLP == "a little bit of russian"|data_BLP=="RUSSIAN"|data_BLP=="russian"] <- "Russian";
  data_BLP[data_BLP == "NDEBELE"] <- "Ndebele";
  data_BLP[data_BLP == "urdu"] <- "Urdu";
  data_BLP[data_BLP == "latvian"] <- "Latvian";
  data_BLP[data_BLP == "Malayam"] <- "Malayan";
  data_BLP[data_BLP == "swahili"] <- "Swahili";
  data_BLP[data_BLP == "serbian"] <- "Serbian";
  data_BLP[data_BLP == "SEPEDI"|data_BLP=="sepedit"] <- "Sepedi";
  data_BLP[data_BLP == "japanese"] <- "Japanese";
  data_BLP[data_BLP == "TSWANA"|data_BLP=="tswana"] <- "Tswana";
  data_BLP[data_BLP == "SHONA"] <- "Shona";
  data_BLP[data_BLP == "sweedish"] <- "Swedish";
  data_BLP[data_BLP == "XItsonga"] <- "Xitsonga";
  data_BLP[data_BLP == "N/A"|data_BLP=="---"] <- "n/a";
  data_BLP["L1"][is.na(data_BLP["L1"])] <- "n/a";
  data_BLP["L2"][is.na(data_BLP["L2"])] <- "n/a";
  data_BLP["L3"][is.na(data_BLP["L3"])] <- "n/a";
  data_BLP["L4"][is.na(data_BLP["L4"])] <- "n/a";
  
  # correcting some participants' demographic information - correction based off of Prolific's information
  data_BLP["Age"][data_BLP["sbj_ID"] == "5aa787c66219a30001c765f8"] <- "24";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5e577e79ce30ae13226e61ae"] <- "24";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5e8c57d9b4483e012006e7aa"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5ecbb4c00bc62403dae2df59"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5ee942381a22491bbb7170f8"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5f219602670e5a0af2cf5237"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5f47e34858dd331165bf9f00"] <- "21";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5f99cee5a2a7d109a1624e10"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5fa4725a186c050edc3bcc20"] <- "23";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5fc2d2d79da439201ab6addc"] <- "24";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5fc44d83862e3e79b02e0438"] <- "24";
  data_BLP["Age"][data_BLP["sbj_ID"] == "5fd9c5c67fa7c74ec42bb318"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6065d7d47409810344f7e6bb"] <- "24";
  data_BLP["Age"][data_BLP["sbj_ID"] == "60883a7e91c0be66dbb96fc8"] <- "23";
  data_BLP["Age"][data_BLP["sbj_ID"] == "608c2e566d92c2aa3543e2d2"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "60e3b18d3d4205b4c52ada56"] <- "24";
  data_BLP["Age"][data_BLP["sbj_ID"] == "611eafa6011b0423f7d7230f"] <- "20";
  data_BLP["Age"][data_BLP["sbj_ID"] == "612a98181f4b6d1cf01f926c"] <- "21";
  data_BLP["Age"][data_BLP["sbj_ID"] == "61301fcb49db2f170cb02b93"] <- "25";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6156b68cc77b48d6693b361c"] <- "21";
  data_BLP["Age"][data_BLP["sbj_ID"] == "616891e25a026e1f7262116c"] <- "22";
  data_BLP["Age"][data_BLP["sbj_ID"] == "6171d922c871ba795b6a4827"] <- "23";
  data_BLP["Gender"][data_BLP["sbj_ID"] == "5aa787c66219a30001c765f8"] <- "Man";
  data_BLP["Gender"][data_BLP["sbj_ID"] == "5bcd11401662020001fe82c1"] <- "Man";
  data_BLP["Gender"][data_BLP["sbj_ID"] == "5e3ff59bf2160b23942ada93"] <- "Man";
  data_BLP["Gender"][data_BLP["sbj_ID"] == "5f5a713d37f71112463ab4d9"] <- "Woman";
  data_BLP["Gender"][data_BLP["sbj_ID"] == "60e9ea97d19e613e60a994da"] <- "Man";
  data_BLP["Gender"][data_BLP["sbj_ID"] == "616eb493bb7e4ab4fa1de8d4"] <- "Woman";
  
  return (data_BLP)
};

data_BLP <- BLP_correction(data_BLP);

# make some variables factors
data_BLP$task <- as.factor(data_BLP$task)
data_BLP$sbj_ID <- as.factor(data_BLP$sbj_ID);
data_BLP$Age <- as.numeric(data_BLP$Age);
data_BLP$Gender <- as.factor(data_BLP$Gender);
data_BLP$Education <- as.factor(data_BLP$Education);
data_BLP$L1 <- as.factor(data_BLP$L1);
data_BLP$L2 <- as.factor(data_BLP$L2);
data_BLP$L3 <- as.factor(data_BLP$L3);
data_BLP$L4 <- as.factor(data_BLP$L4);
data_BLP$otherLs <- as.factor(data_BLP$otherLs);
data_BLP$AttentionL1 <- as.factor(data_BLP$AttentionL1);
data_BLP$AttentionL2 <- as.factor(data_BLP$AttentionL2);
data_BLP$AttentionL3 <- as.factor(data_BLP$AttentionL3);
data_BLP$AttentionL4 <- as.factor(data_BLP$AttentionL4);
summary(data_BLP);
# 112/78 M/F split
# mean age = 22.96
# Portuguese top L1
# English top L2
```

```{r}
scores_list <- subset(data_BLP, select=c('sbj_ID','L1Score','L2Score','L3Score','L4Score')); # combine scores into 1 list
write.csv(scores_list,"BASL_exp1_scores.csv", row.names = FALSE);
use_scores_list <- subset(data_BLP, select=c('sbj_ID','UseL1Score','UseL2Score','UseL3Score','UseL4Score')); # combine use scores into 1 list
write.csv(use_scores_list,"BASL_exp1_usescores.csv", row.names = FALSE);
```

```{r}
# correlations of BLP scores
BLP_scores <- subset(data_BLP,select=c(HistoryL1Score,HistoryL2Score,HistoryL3Score,HistoryL4Score,
                                   UseL1Score,UseL2Score,UseL3Score,UseL4Score,
                                   ProficiencyL1Score,ProficiencyL2Score,ProficiencyL3Score,ProficiencyL4Score,
                                   AttitudeL1Score,AttitudeL2Score,AttitudeL3Score,AttitudeL4Score));
```

```{r}
png('exp1_corrPlot_BLP.png', width=1000, height=1000);
corrplot::corrplot(cor(BLP_scores),type="lower", order="original", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp1_corrPlot_BLP.png"));
```

```{r}
png('exp1_corrPlot_BLP_hclust.png', width=1000, height=1000);
corrplot::corrplot(cor(BLP_scores),type="lower", order="hclust", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp1_corrPlot_BLP_hclust.png"));
```

```{r}
# BLP scores PCA
pca_varimax <- psych::principal(BLP_scores, nfactors=16, rotate='varimax');
data_BLP <- cbind(data_BLP, pca_varimax$scores[,c('RC1','RC9','RC2','RC8','RC3')]);
colnames(data_BLP)[which(names(data_BLP) == "RC1")] <- "RC1_L3";
colnames(data_BLP)[which(names(data_BLP) == "RC9")] <- "RC9_L4";
colnames(data_BLP)[which(names(data_BLP) == "RC2")] <- "RC2_use_L1vsL2";
colnames(data_BLP)[which(names(data_BLP) == "RC8")] <- "RC8_hist_L2"
colnames(data_BLP)[which(names(data_BLP) == "RC3")] <- "RC3_prof_L2"
```

```{r}
# scree plot
scree_data <- data.frame(Component = 1:16,Variance = pca_varimax$values[1:16]);
ggplot(scree_data, aes(x = Component, y = Variance)) +
  geom_line(linewidth=1) +
  geom_point(size=4) +
  labs(title = "Scree Plot", x = "Principal Components", y = "Variance Explained") +
  scale_x_discrete(limits=c(seq(from=1,to=16))) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

```{r}
# biplot of 1st 2 PCs
#biplot(pca_varimax, main="Biplot of First Two Principal Components");
```

```{r}
# loadings plot for 1st 2 PCs
loadings_data <- as.data.frame(pca_varimax$loadings[1:16, ]);
loadings_data$BLP_var <- c("L1 History","L2 History", "L3 History", "L4 History",
                       "L1 Use","L2 Use","L3 Use","L4 Use",
                       "L1 Proficiency","L2 Proficiency","L3 Proficiency","L4 Proficiency",
                       "L1 Attitude","L2 Attitude","L3 Attitude","L4 Attitude");
loadings_data$lang <- c(rep(c("L1","L2","L3","L4"),times=4));
ggplot(loadings_data, aes(x=RC1, y=RC3)) +
  geom_point(size=4,colour=c(rep(c(cols2[100],cols2[310],cols2[200],cols2[285]),times=4))) +
  geom_text_repel(aes(label=rownames(loadings_data)),vjust=2,family="CMU Serif",
            position=position_dodge(width=0.01),force=2,size=10,
            colour=c(rep(c(cols2[100],cols2[310],cols2[200],cols2[285]),times=4))) +
  labs(title="PCA Loadings Plot (PC1 vs PC9)",x="PC1 (L3)",y="PC9 (L4)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),legend.position="none",
        legend.background=element_rect(fill=NA));
```

```{r}
# PC1
ggplot(loadings_data, aes(x=BLP_var, y=RC1, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC1 - L3)",y="PC1 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# PC9
ggplot(loadings_data, aes(x=BLP_var, y=RC9, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC9 - L4)",y="PC9 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# PC2
ggplot(loadings_data, aes(x=BLP_var, y=RC2, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC2 - L1 Use vs L2 Use)",y="PC2 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# PC8
ggplot(loadings_data, aes(x=BLP_var, y=RC8, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC8 - L2 History)",y="PC8 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# PC3
ggplot(loadings_data, aes(x=BLP_var, y=RC3, fill=lang)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=0) +
  scale_fill_manual(values=c("L1"=cols2[100],"L2"=cols2[310],"L3"=cols2[200],"L4"=cols2[285]),
                    name="") +
  labs(title="PCA Loadings Plot (PC3 - L2 Proficiency)",y="PC3 loading",x="BLP variables") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),axis.text.x=element_text(angle=45,vjust=1,hjust=1),
        legend.position=c(0.05,0.9),legend.background=element_rect(fill=NA));
```

```{r}
# Cluster plot of 1st 2 PCs
cluster_data <- data.frame(pca_varimax$scores[, 1:2]);
colnames(cluster_data) <- c("PC1", "PC2");
ggplot(cluster_data, aes(x = PC1, y = PC2)) +
  geom_point() +
  labs(title = "PCA Cluster Plot (First Two PCs)", x = "Principal Component 1", y = "Principal Component 9") +
  theme_minimal();
```

## Multilingual Metrics

```{r}
multilingual_metrics <- data.frame();
for (i in 1:193) {
  temp <- scores_list[which(scores_list$sbj_ID==unique(scores_list$sbj_ID)[i]),];
  sbj_ID <- temp$sbj_ID[1];
  temp_scores <- as.list(temp);
  temp_scores <- temp_scores[-1];
  temp_scores <- unlist(temp_scores);
  
  use_temp <- use_scores_list[which(use_scores_list$sbj_ID==unique(use_scores_list$sbj_ID)[i]),];
  use_temp_scores <- as.list(use_temp);
  use_temp_scores <- use_temp_scores[-1];
  use_temp_scores <- unlist(use_temp_scores);
  
  # variance
  variance <- var(temp_scores,na.rm=TRUE);
  
  # entropy
  entropy <- Entropy(temp_scores,na.rm=TRUE);
  use_entropy <- Entropy(use_temp_scores,na.rm=TRUE);
  
  # multilingual experience
  multiexp <- sum(temp_scores);
  
  # L1 - L2 score
  L1L2 <- abs(temp_scores[[1]]-temp_scores[[2]]);
  
  multilingual_metrics <- rbind(multilingual_metrics, 
      list(sbj_ID,variance,entropy,use_entropy,multiexp,L1L2));
};
names(multilingual_metrics) <- c("sbj_ID","var","ent","use_ent","multiexp","L1_L2_diff");
data_BLP <- merge(data_BLP,multilingual_metrics,by="sbj_ID");
```

### Cosine Similarity

```{r}
cossim <- read.csv("distances_exp1_NOLOWSCORES.csv",header=T,sep=",");
cossim <- subset(cossim, select = -c(X)); # remove redundant column added by Python
names(cossim) <- c('sbj_ID','cossim');
data_BLP <- merge(data_BLP,cossim,by="sbj_ID");

use_cossim <- read.csv("distances_exp1_usescores.csv",header=T,sep=",");
use_cossim <- subset(use_cossim, select = -c(X)); # remove redundant column added by Python
names(use_cossim) <- c('sbj_ID','use_cossim');
data_BLP <- merge(data_BLP,use_cossim,by="sbj_ID");
```

### Multilingual Category

```{r}
data_BLP$category <- "mono";
data_BLP$category[data_BLP$L2Score>0] <- "bi";
data_BLP$category[data_BLP$L3Score>0] <- "tri";
data_BLP$category[data_BLP$L4Score>0] <- "quadri";
data_BLP$category <- factor(data_BLP$category,levels=c("mono","bi","tri","quadri"));
summary(data_BLP$category);
```

### Script

```{r}
diff_script_sbjID <- c('5cbe02ab39447e0001745a5e','5e3ff59bf2160b23942ada93','6147aed5b2a4f748dc2b6ba4');
# n=3
mixed_script_sbjID <- c('5ea171c1a8782801263e7540','5ea9611edec14d052ada0bae','5eb35dff41a381156be161c2','5f0f93938935de000855898b','5f7bd801486f5e1ce581980f','5fc2d2d79da439201ab6addc','5fc44d83862e3e79b02e0438','5fd9c5c67fa7c74ec42bb318','600f0f9c3bfcdc077c924e51','602bb123612bfe330818d4ef','6093cacf9a39751eedd55916','61055020201a7da5a704f7dd','611bdb0fed7c9df6dce28c3f','6163faf9d9ac4586fe776568','616eb493bb7e4ab4fa1de8d4','63ee5d8aaee278de46b7d4cc','64ef422a4789bd6b6b9042ce');
# n=17
sbj_IDs_included <- list(unique(data_BLP$sbj_ID))[[1]];
same_script_sbjID <- sbj_IDs_included[!sbj_IDs_included %in% diff_script_sbjID];
same_script_sbjID <- same_script_sbjID[!same_script_sbjID %in% mixed_script_sbjID];
# n=156
data_BLP$script[data_BLP$sbj_ID %in% diff_script_sbjID] <- 'mixed/diff';
data_BLP$script[data_BLP$sbj_ID %in% mixed_script_sbjID] <- 'mixed/diff';
data_BLP$script[data_BLP$sbj_ID %in% same_script_sbjID] <- 'same';
data_BLP$script <- factor(data_BLP$script,levels=c("same","mixed/diff"));
```

### Metric Comparisons

```{r}
#var
summary(data_BLP$var);
var(data_BLP$var);
```

```{r}
#ent
summary(data_BLP$ent);
var(data_BLP$ent);

cor.test(data_BLP$var,data_BLP$ent,method="pearson"); 
# significantly very strongly negatively correlated 

ggplot(data_BLP, aes(x=sbj_ID,y=ent,colour=category)) +
  geom_point(size=4) +
  labs(x = "Participant ID", y = "Multilingual balance (entropy)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        axis.text.x=element_blank(),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.15,0.25),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual","Bilingual","Trilingual","Quadrilingual"));

hist(data_BLP$ent,breaks=1000,xlab="Multilingual balance (entropy)",
     main="",cex.lab=2,cex.axis=1.5);
# lots at 0 and 1
```

```{r}
#use_ent
summary(data_BLP$use_ent);
var(data_BLP$use_ent);
```

```{r}
#multiexp
summary(data_BLP$multiexp);
var(data_BLP$multiexp);
```

```{r}
#L1_L2_diff
summary(data_BLP$L1_L2_diff);
var(data_BLP$L1_L2_diff);
```

```{r}
#cossim
summary(data_BLP$cossim);
var(data_BLP$cossim);

ggplot(data_BLP, aes(x=sbj_ID,y=cossim,colour=category)) +
  geom_point(size=4) +
  labs(x = "Participant ID", y = "Multilingual balance (cosine similarity)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        axis.text.x=element_blank(),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.15,0.15),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual","Bilingual","Trilingual","Quadrilingual"));

hist(data_BLP$cossim,breaks=1000,
     xlab="Multilingual balance (cosine similarity)",main="",
     cex.lab=2,cex.axis=1.5);
# lots at 1
hist(data_BLP$cossim[data_BLP$category!="mono"],breaks=1000,
     xlab="Multilingual balance (cosine similarity)",main="",
     cex.lab=2,cex.axis=1.5);
# exponential distribution
```

```{r}
ggplot(data_BLP, aes(x=cossim,y=ent,colour=category)) +
  geom_point(size=4) +
  labs(x = "Multilingual balance (cosine similarity)", y = "Multilingual balance (entropy)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.17,0.2),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual (n=22)","Bilingual (n=70)",
                              "Trilingual (n=51)","Quadrilingual (n=41)"));
```

```{r}
#use_cossim
summary(data_BLP$use_cossim);
var(data_BLP$use_cossim);

# cossim & use_cossim
cor.test(data_BLP$cossim,data_BLP$use_cossim,method="pearson");
# significantly strongly positively correlated
```

```{r}
#ent & multiexp
cor.test(data_BLP$ent,data_BLP$multiexp,method="pearson");
# significantly very strongly positively correlated

ggplot(data_BLP, aes(x=multiexp,y=ent,colour=category)) +
  geom_point(size=4) +
  labs(x = "Multilingual experience", y = "Multilingual balance (entropy)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.8,0.2),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual (n=22)","Bilingual (n=70)",
                              "Trilingual (n=51)","Quadrilingual (n=41)"));
```

```{r}
#cossim & multiexp
cor.test(data_BLP$cossim,data_BLP$multiexp,method="pearson");
# not significant

ggplot(data_BLP, aes(x=cossim,y=multiexp,colour=category)) +
  geom_point(size=4) +
  labs(y = "Multilingual experience", x = "Multilingual balance (entropy)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.17,0.8),legend.background=element_rect(fill=NA)) +
  scale_color_manual(values=c(cols2[100],cols2[150],cols2[200],cols2[250]),
                     name="Category",
                     labels=c("Monolingual (n=22)","Bilingual (n=70)",
                              "Trilingual (n=51)","Quadrilingual (n=41)"));
```

```{r}
#cossim & ent
cor.test(data_BLP$cossim,data_BLP$ent,method="pearson");
# no monos:
cor.test(data_BLP$cossim[data_BLP$category!="mono"],data_BLP$ent[data_BLP$category!="mono"],method="pearson");
# negatively correlated
```

```{r}
#ent & use_ent
cor.test(data_BLP$ent,data_BLP$use_ent,method="pearson");
# significantly strongly positively correlated
```

```{r}
# correlations of multilingual metrics
M <- cor(subset(data_BLP,select=c('var','ent','use_ent','multiexp','L1_L2_diff','cossim','use_cossim')));
png('exp1_corrPlot_multimetrics.png', width=1000, height=1000);
corrplot::corrplot(M,type="lower", order="original", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',number.cex=1.5,tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp1_corrPlot_multimetrics.png"));
```

```{r}
png('exp1_corrPlot_multimetrics_hclust.png', width=1000, height=1000);
corrplot::corrplot(M,type="lower", order="hclust", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black', number.cex=1.5,tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp1_corrPlot_multimetrics_hclust.png"));
```

```{r}
# export BLP dataframe
write.csv(data_BLP,"BASL_exp1_BLP.csv", row.names = FALSE);
```

```{r}
# combining BLP & testing scores
data_BLP_shortened <- subset(data_BLP, select=c(sbj_ID,Gender,Age,
                                                HistoryL1Score,HistoryL2Score,HistoryL3Score,HistoryL4Score,
                                                UseL1Score,UseL2Score,UseL3Score,UseL4Score,
                                                ProficiencyL1Score,ProficiencyL2Score,ProficiencyL3Score,ProficiencyL4Score,
                                                AttitudeL1Score,AttitudeL2Score,AttitudeL3Score,AttitudeL4Score,
                                                L1Score,L2Score,L3Score,L4Score,category,script,
                                                var,ent,use_ent,multiexp,L1_L2_diff,cossim,use_cossim,
                                                RC1_L3,RC9_L4,RC2_use_L1vsL2,RC8_hist_L2,RC3_prof_L2));
data_BLP_testing <- list(data_testing,data_BLP_shortened) %>% reduce(inner_join, by='sbj_ID');
data_BLP_familiarity <- list(data_familiarity,data_BLP_shortened) %>% reduce(inner_join, by='sbj_ID');
```

```{r}
# correlations of BLP metrics with testing scores
M <- cor(subset(data_BLP_testing,select=c(score_2M,dprime,c,
                                          var,ent,use_ent,multiexp,L1_L2_diff,cossim,use_cossim,
                                          RC1_L3,RC9_L4,RC2_use_L1vsL2,RC8_hist_L2,RC3_prof_L2)));
png('exp1_corrPlot_BLP_testing.png', width=1000, height=1000);
corrplot::corrplot(M,type="lower", order="original", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp1_corrPlot_BLP_testing.png"));
```

```{r}
png('exp1_corrPlot_BLP_testing_hclust.png', width=1000, height=1000);
corrplot::corrplot(M,type="lower", order="hclust", diag=T, method="color", outline=F, addgrid.col=F, tl.col='black', tl.pos='ld', addCoef.col='black',tl.cex=1.5);
dev.off();
grid.raster(readPNG("exp1_corrPlot_BLP_testing_hclust.png"));
```

```{r}
# export BLP testing dataframe
write.csv(data_BLP_testing,"BASL_exp1_BLPtesting.csv", row.names = FALSE);
```

# LINEAR MODELLING

## "Yes" Responses LMERs

### Testing Conditions

```{r}
lm_TestingConditions <- glmer(observed ~ testing_condition + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_TestingConditions)
effect_conditions <- as.data.frame(effect('testing_condition',
                                          lm_TestingConditions, confint=list(alpha=.95)),
                                   xlevels = list(testing_condition=c('0M','1M','2M')));
effect_conditions
export_output(model=lm_TestingConditions,name="Exp. 1 `Yes' responses - Conditions",
              pred_levels=c('0M','1M','2M'),pred_type='categorical',
              outcome_levels=c('0M','1M','2M'));
```

### Gender

```{r}
lm_Gender <- glmer(observed ~ scale(trialn) + testing_condition*Gender + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_Gender); 
export_output(model=lm_Gender,name="Exp. 1 `Yes' responses - Gender",
              pred_levels=c('Man','Other','Woman'),pred_type='categorical',
              outcome_levels=c('0M','1M','2M'));
```

### Age

```{r}
lm_Age <- glmer(observed ~ scale(trialn) + testing_condition*scale(Age) + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_Age);
export_output(model=lm_Age,name="Exp. 1 `Yes' responses - Age",
              pred_levels=c('scale(Age)'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC1

```{r}
lm_RC1 <- glmer(observed ~ scale(trialn) + testing_condition*RC1_L3 + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC1);
export_output(model=lm_RC1,name="Exp. 1 `Yes' responses - PC1 (L3)",
              pred_levels=c('PC1_L3'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC9

```{r}
lm_RC9 <- glmer(observed ~ testing_condition*RC9_L4 + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC9); 
export_output(model=lm_RC9,name="Exp. 1 `Yes' responses - PC9 (L4)",
              pred_levels=c('PC9_L4'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC2

```{r}
lm_RC2 <- glmer(observed ~ scale(trialn) + testing_condition*RC2_use_L1vsL2 + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC2); 
export_output(model=lm_RC2,name="Exp. 1 `Yes' responses - PC2 (L1 vs L2 Use)",
              pred_levels=c('PC2_L1vsL2_Use'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC8

```{r}
lm_RC8 <- glmer(observed ~ scale(trialn) + testing_condition*RC8_hist_L2 + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
export_output(model=lm_RC8,name="Exp. 1 `Yes' responses - PC8 (L2 History)",
              pred_levels=c('PC8_L2_History'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### PC3

```{r}
lm_RC3 <- glmer(observed ~ scale(trialn) + testing_condition*RC3_prof_L2 + (1+testing_condition|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_RC3); 
export_output(model=lm_RC3,name="Exp. 1 `Yes' responses - PC3 (L2 Proficiency)",
              pred_levels=c('PC3_L2_Proficiency'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### Entropy

```{r}
lm_ent <- glmer(observed ~ testing_condition*ent + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_ent);
export_output(model=lm_ent,name="Exp. 1 `Yes' responses - Multilingual balance (Entropy)",
              pred_levels=c('Entropy'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### Use Entropy

```{r}
lm_use_ent <- glmer(observed ~ testing_condition*use_ent + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_use_ent);
```

### Multilingual Experience

```{r}
lm_multiexp <- glmer(observed ~ scale(trialn) + testing_condition*scale(multiexp) + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_multiexp);
export_output(model=lm_multiexp,name="Exp. 1 `Yes' responses - Multilingual experience",
              pred_levels=c('scale(Multilingual experience)'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### L1-L2 Difference

```{r}
lm_L1L2diff <- glmer(observed ~ testing_condition*scale(L1_L2_diff) + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_L1L2diff);
export_output(model=lm_L1L2diff,name="Exp. 1 `Yes' responses - Bilingual balance (L1-L2 difference)",
              pred_levels=c('scale(L1-L2 difference)'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### Cosine Similarity

```{r}
lm_cossim <- glmer(observed ~ testing_condition*cossim + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_cossim);
export_output(model=lm_cossim,name="Exp. 1 `Yes' responses - Multilingual balance (cosine similarity)",
              pred_levels=c('Cosine similarity'),pred_type='continuous',
              outcome_levels=c('0M','1M','2M'));
```

### Use Cosine Similarity

```{r}
lm_use_cossim <- glmer(observed ~ testing_condition*use_cossim + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial',control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)));
summary(lm_use_cossim);
```

### Script

```{r}
lm_script <- glmer(observed ~ scale(trialn) + testing_condition*script + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial');
summary(lm_script);
export_output(model=lm_script,name="Exp. 1 `Yes' responses - Script",
              pred_levels=c('Same script','Different script'),pred_type='categorical',
              outcome_levels=c('0M','1M','2M'));
```

### Category

```{r}
lm_category <- glmer(observed ~ testing_condition*category + (1|sbj_ID), data=subset(data_BLP_testing, rt>300 & rt<3000), family='binomial',control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)));
summary(lm_category);
export_output(model=lm_category,name="Exp. 1 `Yes' responses - Category",
              pred_levels=c('Monolingual','Bilingual','Trilingual','Quadrilingual'),
              pred_type='categorical',
              outcome_levels=c('0M','1M','2M'));
```

## 2M Responses LMERs

```{r}
lm_2M <- glmer(observed ~ scale(trialn) + expected + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M);
effect_2M <- as.data.frame(effect('expected',lm_2M,confint=list(alpha=.95)),
                           xlevels = list(expected=c(0,1)));
export_output(model=lm_2M,name="Exp. 1 2M",
              pred_levels=c('between_language','within_language'),
              pred_type='categorical',
              outcome_levels=c('between_language','within_language'));
```

### Gender

```{r}
lm_2M_Gender <- glmer(observed ~ scale(trialn) + expected*Gender + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_Gender);
export_output(model=lm_2M_Gender,name="Exp. 1 2M - Gender",
              pred_levels=c('Man','Other','Woman'),pred_type='categorical',
              outcome_levels=c('between_language','within_language'));
```

### Age

```{r}
lm_2M_Age <- glmer(observed ~ scale(trialn) + expected*scale(Age) + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_Age);
export_output(model=lm_2M_Age,name="Exp. 1 2M - Age",
              pred_levels=c('scale(Age)'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC1

```{r}
lm_2M_RC1 <- glmer(observed ~ scale(trialn) + expected*RC1_L3 + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC1);
export_output(model=lm_2M_RC1,name="Exp. 1 2M - PC1 (L3)",
              pred_levels=c('PC1_L3'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC9

```{r}
lm_2M_RC9 <- glmer(observed ~ scale(trialn) + expected*RC9_L4 + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC9);
export_output(model=lm_2M_RC9,name="Exp. 1 2M - PC9 (L4)",
              pred_levels=c('PC9_L4'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC2

```{r}
lm_2M_RC2 <- glmer(observed ~ scale(trialn) + expected*RC2_use_L1vsL2 + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC2);
export_output(model=lm_2M_RC2,name="Exp. 1 2M - PC2 (L1 vs L2 Use)",
              pred_levels=c('PC2_L1vsL2_Use'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC8

```{r}
lm_2M_RC8 <- glmer(observed ~ scale(trialn) + expected*RC8_hist_L2 + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC8);
export_output(model=lm_2M_RC8,name="Exp. 1 2M - PC8 (L2 History)",
              pred_levels=c('PC8_L2_History'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### PC3

```{r}
lm_2M_RC3 <- glmer(observed ~ scale(trialn) + expected*RC3_prof_L2 + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_RC3);
export_output(model=lm_2M_RC3,name="Exp. 1 2M - PC3 (L2 Proficiency)",
              pred_levels=c('PC3_L2_Proficiency'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### Entropy

```{r}
lm_2M_ent <- glmer(observed ~ scale(trialn) + expected*ent + (1+expected|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_ent);
export_output(model=lm_2M_ent,name="Exp. 1 2M - Multilingual balance (Entropy)",
              pred_levels=c('Entropy'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### Use Entropy

```{r}
lm_2M_use_ent <- glmer(observed ~ scale(trialn) + expected*use_ent + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_use_ent); 
```

### Multilingual Experience

```{r}
lm_2M_multiexp <- glmer(observed ~ scale(trialn) + expected*scale(multiexp) + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_multiexp);
export_output(model=lm_2M_multiexp,name="Exp. 1 2M - Multilingual experience",
              pred_levels=c('scale(Multilingual experience)'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### L1-L2 Difference

```{r}
lm_2M_L1L2diff <- glmer(observed ~ scale(trialn) + expected*scale(L1_L2_diff) + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_L1L2diff);
export_output(model=lm_2M_L1L2diff,name="Exp. 1 2M - Bilingual Balance (L1-L2 difference)",
              pred_levels=c('scale(L1-L2 difference)'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### Cosine Similarity

```{r}
lm_2M_cossim <- glmer(observed ~ scale(trialn) + expected*scale(cossim) + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_cossim);
export_output(model=lm_2M_cossim,name="Exp. 1 2M - Multilingual balance (cosine similarity)",
              pred_levels=c('scale(Cosine similarity)'),pred_type='continuous',
              outcome_levels=c('between_language','within_language'));
```

### Use Cosine Similarity

```{r}
lm_2M_use_cossim <- glmer(observed ~ scale(trialn) + expected*scale(use_cossim) + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_use_cossim); 
```

### Script

```{r}
lm_2M_script <- glmer(observed ~ scale(trialn) + expected*script + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_script);
export_output(model=lm_2M_script,name="Exp. 1 2M - Script",
              pred_levels=c('Same script','Different script'),pred_type='categorical',
              outcome_levels=c('between_language','within_language'));
```

### Category

```{r}
lm_2M_category <- glmer(observed ~ expected*category + (1|sbj_ID), data=data_BLP_testing[data_BLP_testing$testing_condition=='2M'& data_BLP_testing$rt>300 & data_BLP_testing$rt<3000,], family='binomial');
summary(lm_2M_category);
export_output(model=lm_2M_category,name="Exp. 1 2M - Category",
              pred_levels=c('Monolingual','Bilingual','Trilingual','Quadrilingual'),
              pred_type='categorical',
              outcome_levels=c('between_language','within_language'));
```

## Familiarity Responses LMERs

```{r}
data_BLP_familiarity$correct_numerical <- as.numeric(data_BLP_familiarity$correct);
```

### Gender

```{r}
lm_fam_Gender <- glmer(correct ~ scale(trialn) + Gender + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_Gender);
export_output(model=lm_fam_Gender,name="Exp. 1 Familiarity - Gender",
              pred_levels=c('Man','Other','Woman'),pred_type='categorical',
              outcome_levels=c('wrong','right'));
```

### Age

```{r}
lm_fam_Age <- glmer(correct ~ scale(trialn) + scale(Age) + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_Age);
export_output(model=lm_fam_Age,name="Exp. 1 Familiarity - Age",
              pred_levels=c('scale(Age)'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC1

```{r}
lm_fam_RC1 <- glmer(correct ~ scale(trialn) + RC1_L3 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC1);
export_output(model=lm_fam_RC1,name="Exp. 1 Familiarity - PC1 (L3)",
              pred_levels=c('PC1_L3'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC9

```{r}
lm_fam_RC9 <- glmer(correct ~ scale(trialn) + RC9_L4 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC9);
export_output(model=lm_fam_RC9,name="Exp. 1 Familiarity - PC9 (L4)",
              pred_levels=c('PC9_L4'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC2

```{r}
lm_fam_RC2 <- glmer(correct ~ scale(trialn) + RC2_use_L1vsL2 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC2);
export_output(model=lm_fam_RC2,name="Exp. 1 Familiarity - PC2 (L1 vs L2 Use)",
              pred_levels=c('PC2_L1vsL2_Use'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC8

```{r}
lm_fam_RC8 <- glmer(correct ~ scale(trialn) + RC8_hist_L2 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC8);
export_output(model=lm_fam_RC8,name="Exp. 1 Familiarity - PC8 (L2 History)",
              pred_levels=c('PC8_L2_History'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### PC3

```{r}
lm_fam_RC3 <- glmer(correct ~ scale(trialn) + RC3_prof_L2 + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_RC3);
export_output(model=lm_fam_Age,name="Exp. 1 Familiarity - PC3 (L2 Proficiency)",
              pred_levels=c('PC3_L2_Proficicent'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### Entropy

```{r}
lm_fam_ent <- glmer(correct ~ scale(trialn) + ent + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_ent);
export_output(model=lm_fam_ent,name="Exp. 1 Familiarity - Multilingual balance (entropy)",
              pred_levels=c('Entropy'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### Use Entropy

```{r}
lm_fam_use_ent <- glmer(correct ~ scale(trialn) + use_ent + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_use_ent); 
```

### Multilingual Experience

```{r}
lm_fam_multiexp <- glmer(correct ~ scale(trialn) + scale(multiexp) + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_multiexp);
export_output(model=lm_fam_multiexp,name="Exp. 1 Familiarity - Multilingual experience",
              pred_levels=c('scale(Multilingual experience)'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### L1-L2 Difference

```{r}
lm_fam_L1L2diff <- glmer(correct ~ scale(trialn) + scale(L1_L2_diff) + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_L1L2diff);
export_output(model=lm_fam_L1L2diff,name="Exp. 1 Familiarity - Bilingual balance (L1-L2 difference)",
              pred_levels=c('scale(L1-L2 difference)'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### Cosine Similarity

```{r}
lm_fam_cossim <- glmer(correct ~ scale(trialn) + cossim + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_cossim); 
export_output(model=lm_fam_cossim,name="Exp. 1 Familiarity - Multilingual balance (cosine similarity)",
              pred_levels=c('Cosine similarity'),pred_type='continuous',
              outcome_levels=c('wrong','right'));
```

### Use Cosine Similarity

```{r}
lm_fam_use_cossim <- glmer(correct ~ scale(trialn) + use_cossim + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_use_cossim); 
```

### Script

```{r}
lm_fam_script <- glmer(correct ~ scale(trialn) + script + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_script);
export_output(model=lm_fam_script,name="Exp. 1 Familiarity - Script",
              pred_levels=c('Same script','Different script'),pred_type='categorical',
              outcome_levels=c('wrong','right'));
```

### Category

```{r}
lm_fam_category <- glmer(correct ~ scale(trialn) + category + (1|sbj_ID), data=data_BLP_familiarity, family='binomial');
summary(lm_fam_category);
export_output(model=lm_fam_category,name="Exp. 1 Familiarity - Category",
              pred_levels=c('Monolingual','Bilingual','Trilingual','Quadrilingual'),
              pred_type='categorical',outcome_levels=c('wrong','right'));
```

# EXPLORATION OF SIGNIFICANT EFFECTS

```{r}
data_testing_conditions_BLP <- merge(data_testing_conditions,subset(data_BLP,select=c(sbj_ID,Gender,Age,RC2_use_L1vsL2,RC8_hist_L2,RC3_prof_L2,multiexp,L1_L2_diff,ent)),by="sbj_ID");
```

## "Yes" Responses

### "Yes" - Testing Conditions

```{r}
ggplot(data_testing_conditions, aes(x=condition, y=score, fill=condition)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_violin(alpha=0.75) +
  
  geom_errorbar(aes(x=1,ymin=effect_conditions$lower[[1]],
                    ymax=effect_conditions$upper[[1]]),width=.1) + # 0M
  annotate("point",x=1,y=effect_conditions$fit[[1]],colour=cols2[100],size=2) + # 0M
  
  geom_errorbar(aes(x=2,ymin=effect_conditions$lower[[2]],
                    ymax=effect_conditions$upper[[2]]),width=.1) + # 1M
  annotate("point",x=2,y=effect_conditions$fit[[2]],colour=cols2[200],size=2) + # 1M
  
  geom_errorbar(aes(x=3,ymin=effect_conditions$lower[[3]],
                    ymax=effect_conditions$upper[[3]]),width=.1) + # 2M
  annotate("point",x=3,y=effect_conditions$fit[[3]],colour="#004D40FF",size=2) + # 2M
  
  ylim(0,1.01) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF")) +
  labs(x = "Testing condition", y = 'Proportion of "yes" responses') +
  scale_x_discrete(labels=c("0M", "1M", "2M")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position = "none");
```

### "Yes" - Gender

```{r}
ggplot(data_testing_conditions_BLP, aes(x=condition,y=score,fill=Gender,group=interaction(condition,Gender))) +
  scale_fill_manual(values=c(cols2[400],cols2[310],cols2[200])) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_boxplot(alpha = 0.75, width=0.75) +
  geom_point(position = position_dodge(width=0.75),size=2) +
  labs(x = "Condition", y = 'Proportion of "yes" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.9,0.1),legend.background=element_rect(fill=NA)) +
  ylim(0,1.05) +
  coord_cartesian(expand = FALSE) +
  scale_x_discrete(labels=c("0M", "1M", "2M"));
# too few Gender = Other datapoints to be meaningful
```

### "Yes" - Age

```{r}
effect_Age <- as.data.frame(effect('testing_condition*scale(Age)',
                                   lm_Age, confint=list(alpha=.95)),
                            xlevels = list(Age = 18:25,
                                           testing_condition=c('0M','1M','2M')));

ggplot(effect_Age, aes(x=Age,y=fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  labs(x = "Age", y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.1,0.1),legend.background=element_rect(fill=NA));
# Older -> bigger morph familiarity effect
```

### "Yes" - PC8

```{r}
effect_RC8 <- as.data.frame(effect('testing_condition*RC8_hist_L2',
                                   lm_RC8, confint=list(alpha=.95)),
                            xlevels = list(RC8_hist_L2 = -2.1:3.1,
                                           testing_condition=c('0M','1M','2M')));

ggplot(effect_RC8, aes(x=RC8_hist_L2,y=fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  labs(x = "RC8: L2 History", y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.1,0.9),legend.background=element_rect(fill=NA));
# Earlier bilingual = more "yes" responses overall
```

### "Yes" - PC3

```{r}
effect_RC3 <- as.data.frame(effect('testing_condition*RC3_prof_L2',
                                        lm_RC3, confint=list(alpha=.95)),
                                 xlevels = list(RC3_prof_L2 = -4.1:1.6,
                                                testing_condition=c('0M','1M','2M')));

ggplot(effect_RC3, aes(x=RC3_prof_L2,y=fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  labs(x = "RC3: L2 Proficiency", y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.1,0.9),legend.background=element_rect(fill=NA)); 
# More proficient L2 = stronger morpheme familiarity effect
```

### "Yes" - L1-L2 Difference

```{r}
effect_L1L2diff <- as.data.frame(effect('testing_condition*scale(L1_L2_diff)',
                                        lm_L1L2diff, confint=list(alpha=.95)),
                                 xlevels = list(L1_L2_diff = 0:210,
                                                testing_condition=c('0M','1M','2M')));

ggplot(effect_L1L2diff, aes(x = L1_L2_diff, y = fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.9,0.9),legend.background=element_rect(fill=NA)) +
  labs(x = 'Bilingual balance (L1-L2 difference)', y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4');
# More bilingual balance = stronger morph familiarity effect
```

### "Yes" - Entropy

```{r}
effect_ent <- as.data.frame(effect('testing_condition*ent',
                                        lm_ent, confint=list(alpha=.95)),
                                 xlevels = list(ent = 0:2,
                                                testing_condition=c('0M','1M','2M')));

ggplot(effect_ent, aes(x = ent, y = fit)) +
  geom_hline(yintercept=0.5, linetype="dashed", 
             color = "darkgray",lwd=1.25) +
  geom_line(aes(color = testing_condition), lwd = 2) +
  geom_ribbon(aes(ymin = lower, ymax = upper, fill = testing_condition), alpha = .5) +
  scale_color_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                     name="Condition",labels=c("0M","1M","2M")) +
  scale_fill_manual(values=c(cols2[100],cols2[200],"#004D40FF"),
                    name="Condition",labels=c("0M","1M","2M")) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position=c(0.1,0.9),legend.background=element_rect(fill=NA)) +
  labs(x = 'Multilingual balance (entropy)', y = 'Proportion of "yes" responses', title = 'Fitted Line - Lme4');
# More multilingual balance = stronger morph familiarity effect?
```

## 2M Responses

```{r}
BLP_2Mscores <- data_BLP_testing[!duplicated(data_BLP_testing$sbj_ID), ];

data_testing_2M_aggr <- data_testing_2M_aggr[data_testing_2M_aggr$response=="meanYes",];
```

```{r}
ggplot(data_testing_2M_aggr, aes(x=expected, y=meanValue, fill=expected)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  
  geom_errorbar(aes(x=1,ymin=effect_2M$lower[[1]],ymax=effect_2M$upper[[1]]),
                width=.1) + # false alarm
  annotate("point",x=1,y=effect_2M$fit[[1]],colour="darkred",size=2) + # false alarm
  
  geom_errorbar(aes(x=2,ymin=effect_2M$lower[[2]],ymax=effect_2M$upper[[2]]),
                width=.1) + # hit
  annotate("point",x=2,y=effect_2M$fit[[2]],colour="lightblue",size=2) + # hit
  
  scale_fill_manual(values=c(cols2[100],cols2[200])) +
  scale_x_discrete(labels=c('Between-language', 'Within-language')) +
  labs(x = "String nature", y = 'Proportion of "yes" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="none",legend.background=element_rect(fill=NA));
```

### 2M - PC8

```{r}
ggplot(data_BLP_testing, aes(x=RC8_hist_L2,y=yes_2M)) +
  geom_hline(yintercept=50,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "PC8: L2 History", y = 'Percent of 2M "yes" responses') +
  ylim(0,101) + 
  xlim(min(data_BLP_testing$RC8_hist_L2)-0.1,max(data_BLP_testing$RC8_hist_L2)+0.1) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### 2M - PC3

```{r}
ggplot(data_BLP_testing, aes(x=RC3_prof_L2,y=yes_2M)) +
  geom_hline(yintercept=50,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "PC8: L2 History", y = 'Percent of 2M "yes" responses') +
  ylim(0,101) +
  xlim(min(data_BLP_testing$RC3_prof_L2)-0.1,max(data_BLP_testing$RC3_prof_L2)+0.1) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size =20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

```{r}
ggplot(data_BLP_testing, aes(x=RC3_prof_L2,y=score_2M)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "PC8: L2 History", y = '2M accuracy') +
  ylim(min(data_BLP_testing$score_2M)-0.05,max(data_BLP_testing$score_2M)+0.05) +
  xlim(min(data_BLP_testing$RC3_prof_L2)-0.1,max(data_BLP_testing$RC3_prof_L2)+0.1) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### 2M -L1-L2 Difference

```{r}
ggplot(data_BLP_testing, aes(x=L1_L2_diff,y=yes_2M)) +
  geom_hline(yintercept=50,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "Bilingual balance (L1-L2 difference)", y = 'Percent of 2M "yes" responses') +
  ylim(0,101) + 
  xlim(min(data_BLP_testing$L1_L2_diff)-2,max(data_BLP_testing$L1_L2_diff)+2) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="inside",legend.position.inside = c(0.85,0.09),
        legend.background=element_rect(fill=NA));
```

### 2M - Script

```{r}
ggplot(data_BLP_testing, aes(x=script,y=score_2M)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_boxplot(fill="darkgrey") +
  labs(x = "Script", y = '2M accuracy') +
  scale_x_discrete(labels=c('Same', 'Different')) +
  ylim(0,1.1) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

```{r}
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$script=='same'],mu=0.5);
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$script=='diff/mixed'],mu=0.5);
```

```{r}
data_testing_2M_script_aggr <- data_BLP_testing %>% 
  mutate(correct01 = case_when(correct == TRUE ~ 1,
                               correct == FALSE ~ 0),
         yesno01 = case_when(observed == 'between_lang' ~ 0,
                             observed == 'within_lang' ~ 1)) %>% 
  filter(testing_condition == '2M') %>% 
  group_by(expected, sbj_ID, script) %>% 
  dplyr::summarise(meanCorrect = mean(correct01), se = sd(correct01/sqrt(n())),
                   meanYes = mean(yesno01), se = sd(yesno01/sqrt(n()))) %>% 
  mutate(meanNo = 1 - meanYes);
data_testing_2M_script_aggr <- data_testing_2M_script_aggr %>%
  pivot_longer(
    cols = c(meanYes, meanNo),
    names_to = "response",
    values_to = "meanValue"
  );
```

```{r}
ggplot(data_testing_2M_script_aggr[data_testing_2M_script_aggr$response=="meanYes",], aes(x=expected, y=meanValue, fill=script)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  geom_boxplot(position=position_dodge(width=1),width=0.25) +
  scale_fill_manual(name="Script",labels=c('Same','Different'),values=c(cols2[400],cols2[310])) +
  scale_x_discrete(labels=c('Between-language', 'Within-language')) +
  labs(x = "String nature", y = 'Proportion of "within-language" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),legend.position="inside",
        legend.position.inside=c(0.1,0.1),legend.background=element_rect(fill=NA));
```

### 2M - Category

```{r}
ggplot(data_BLP_testing, aes(x=category,y=score_2M)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_boxplot(fill="darkgrey") +
  labs(x = "Script", y = '2M accuracy') +
  scale_x_discrete(labels=c('Monolingual','Bilingual','Trilingual','Quadrilingual')) +
  ylim(min(data_BLP_testing$score_2M)-0.05,max(data_BLP_testing$score_2M)+0.05) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

```{r}
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$category=='mono'],mu=0.5);
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$category=='bi'],mu=0.5);
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$category=='tri'],mu=0.5);
t.test(BLP_2Mscores$score_2M[BLP_2Mscores$category=='quadri'],mu=0.5);
```

```{r}
t.test(BLP_2Mscores$dprime[BLP_2Mscores$category=='mono'],mu=0);
t.test(BLP_2Mscores$dprime[BLP_2Mscores$category=='bi'],mu=0);
t.test(BLP_2Mscores$dprime[BLP_2Mscores$category=='tri'],mu=0);
t.test(BLP_2Mscores$dprime[BLP_2Mscores$category=='quadri'],mu=0);
```

```{r}
data_testing_2M_category_aggr <- data_BLP_testing %>% 
  mutate(correct01 = case_when(correct == TRUE ~ 1,
                               correct == FALSE ~ 0),
         yesno01 = case_when(observed == 'between_lang' ~ 0,
                             observed == 'within_lang' ~ 1)) %>% 
  filter(testing_condition == '2M') %>% 
  group_by(expected, sbj_ID, category) %>% 
  dplyr::summarise(meanCorrect = mean(correct01), se = sd(correct01/sqrt(n())),
                   meanYes = mean(yesno01), se = sd(yesno01/sqrt(n()))) %>% 
  mutate(meanNo = 1 - meanYes);
```

```{r}
ggplot(data_testing_2M_category_aggr, aes(x=expected, y=meanCorrect, fill=expected)) +
  geom_hline(yintercept=0.5, linetype="dashed", color="darkgrey",lwd=1.25) +
  geom_violin(alpha=0.75,width=1) +
  
  geom_errorbar(aes(x=1,ymin=effect_2M$lower[[1]],ymax=effect_2M$upper[[1]]),
                width=.1) + # false alarm
  annotate("point",x=1,y=effect_2M$fit[[1]],colour="darkred",size=2) + # false alarm
  
  geom_errorbar(aes(x=2,ymin=effect_2M$lower[[2]],ymax=effect_2M$upper[[2]]),
                width=.1) + # hit
  annotate("point",x=2,y=effect_2M$fit[[2]],colour="lightblue",size=2) + # hit
  
  scale_fill_manual(values=c(cols2[100],cols2[200])) +
  scale_x_discrete(labels=c('Between-language', 'Within-language')) +
  labs(x = "String nature", y = 'Proportion of "yes" responses') +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.position="none",legend.background=element_rect(fill=NA))+
  facet_wrap(~category);
```

## Familiarity Responses

```{r}
data_BLP_familiarity <- merge(data_BLP_familiarity,data_familiarity_means,by="sbj_ID");
```

### Familiarity - Gender

```{r}
ggplot(data_BLP_familiarity, aes(x=Gender,y=fam_mean)) +
  geom_hline(yintercept=0.5,linetype="dashed",color="darkgrey") +
  geom_boxplot(fill="darkgrey") +
  labs(x = "Gender", y = 'Familiarity accuracy') +
  scale_x_discrete(labels=c('Men', 'Other','Women')) +
  ylim(min(data_BLP_familiarity$familiarity_mean)-0.05,max(data_BLP_familiarity$familiarity_mean)+0.05) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

### Familiarity - Age

```{r}
BLP_fam <- data_BLP_familiarity[!duplicated(data_BLP_familiarity$sbj_ID), ];
```

```{r}
ggplot(data_BLP_familiarity, aes(x=Age,y=familiarity_mean)) +
  geom_hline(yintercept=0.50,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "Age", y = 'Familiarity accuracy') +
  ylim(0,1) + 
  xlim(min(data_BLP_familiarity$Age)-0.1,max(data_BLP_familiarity$Age)+0.1) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

### Familiarity - PC3

```{r}
ggplot(data_BLP_familiarity, aes(x=RC3_prof_L2,y=familiarity_mean)) +
  geom_hline(yintercept=0.50,linetype="dashed",color="darkgrey") +
  geom_point(size=2) +
  geom_smooth(method="lm",formula=y~x,color="red") +
  labs(x = "PC3 (L2 Proficiency)", y = 'Familiarity accuracy') +
  ylim(0,1) + 
  xlim(min(data_BLP_familiarity$RC3_prof_L2)-0.1,max(data_BLP_familiarity$RC3_prof_L2)+0.1) +
  coord_cartesian(expand = FALSE) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"),
        axis.text = element_text(family = "CMU Serif", size = 20, color = "black"),
        text=element_text(family="CMU Serif",size=20),
        legend.background=element_rect(fill=NA));
```

# Clustering Tree

```{r}
data_BLP_short <- subset(data_BLP, select=c(HistoryL1Score,HistoryL2Score,HistoryL3Score,HistoryL4Score,
                                            UseL1Score,UseL2Score,UseL3Score,UseL4Score,
                                            ProficiencyL1Score,ProficiencyL2Score,ProficiencyL3Score,ProficiencyL4Score,
                                            AttitudeL1Score,AttitudeL2Score,AttitudeL3Score,AttitudeL4Score,
                                            L1Score,L2Score,L3Score,L4Score,
                                            var,ent,use_ent,cossim,use_cossim,multiexp,L1_L2_diff,
                                            RC1_L3,RC9_L4,RC2_use_L1vsL2,RC8_hist_L2,RC3_prof_L2));
plot(varclus(as.matrix(data_BLP_short)))
```
